---
title: "pilotC_analysis"
output: html_document
date: "2024-07-03"
---
This is the initial analysis on the pilot C participants (the SONA ones). The spatial recall was 4 squares at a time, 
and the visual search was conjunction only and 24 items only. 

The setup was:
8 spatial recall practice
16 visual search practice

13 blocks
- 20 visual search per block
- 10 spatial recall per block

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
##library(jsonlite)
library("broom")      # for tidying up linear models 
library("car")        # for running ANOVAs
library("afex")       # also for running ANOVAs
library("emmeans")    # for calculating constrasts

# set the default ggplot theme 
theme_set(theme_classic())
```
**reading in the data**
``` {r data_wrangling}
setwd("../../data/pilotC/")

csv_files <- list.files(pattern = "\\.csv$")

# Function to read a CSV file and convert all columns to character type
read_csv_as_character <- function(file) {
  df <- read.csv(file, stringsAsFactors = FALSE)
  df[] <- lapply(df, as.character)
  return(df)
}

df_all <- bind_rows(lapply(csv_files,read_csv_as_character))
```

**pre-processing the data**
First I will anonymize the data and remove unneccesary columns:
``` {r data_wrangling}
anonymize_clean <- function(df) {
  df <- df %>%
    select(-recorded_at,-ip,-user_agent,-referer,-sequence_length,
         -accept_language,-device,-internal_node_id,-view_history,
         -source_code_version, -contains("browser"),-contains("platform"),
         -contains("screen"),-contains("width"),-contains("height"),
         -contains("failed"),-condition,-success,-event_history)
  return(df)
}
df_all <- anonymize_clean(df_all)
```

Now I will take out the practice trials and save them to a different df, I will also remove practice and all other trial types (other than sr or vs) from my dataframe
``` {r data_wrangling}
# save practice to practice_runs_df
practice_runs_df <- df_all %>%
  filter(practice == "true")

# save feedback to a df
# make a column for how much they rated vs and sr difficulty and boringness
feedback_df <- df_all %>%
  filter(trial_type == "survey-text") %>%
  filter(str_detect(response, "bid_decision") | str_detect(response, "game_description") | str_detect(response, "boring"))
feedback_df <- feedback_df %>%
  mutate(response = map(response, ~ jsonlite::fromJSON(.))) %>%
  unnest_wider(response)

feedback_temp_sr <- feedback_df %>%
  filter(!is.na(sr_boring)) %>%
  select(run_id, sr_boring, sr_difficult)
feedback_temp_vs <- feedback_df %>%
  filter(!is.na(vs_boring)) %>%
  select(run_id, vs_boring, vs_difficult)

df_all <- merge(df_all, feedback_temp_sr, by = "run_id")
df_all <- merge(df_all, feedback_temp_vs, by = "run_id")

# make a column for average practice score per participant and put it into the main df
temp <- practice_runs_df %>%
  select(run_id, trial_type, score_an, correct_trial) %>%
  mutate(correct = ifelse(trial_type == "spatial-recall",as.integer(score_an),ifelse(correct_trial=="null",0,as.integer(correct_trial)))) %>%
  select(run_id, trial_type, correct) %>%
  group_by(run_id, trial_type) %>%
  summarise(avg_correct = mean(correct)) %>%
  mutate(sr_practice_accuracy = ifelse(trial_type == "spatial-recall",avg_correct,NA),vs_practice_accuracy = ifelse(trial_type != "spatial-recall",avg_correct,NA)) %>%
  ungroup() %>%
  select(run_id, sr_practice_accuracy, vs_practice_accuracy) %>%
  group_by(run_id) %>%
  summarise(
    sr_practice_accuracy = max(sr_practice_accuracy, na.rm = TRUE),
    vs_practice_accuracy = max(vs_practice_accuracy, na.rm = TRUE)
  ) %>%
  ungroup()
df_all <- merge(df_all, temp, by = "run_id")


# remove practice & other non-task rows from df
df_all_cleaned <- df_all %>%
  filter(trial_type != "instructions", trial_type != "preload", 
           trial_type != "survey-multi-choice",
           (trial_type != 'html-keyboard-response' | trial_id =='test_trial'),
           (trial_type != 'html-button-response'),
           !grepl("screen", trial_type, ignore.case = TRUE)) %>%
    filter(practice != "true") %>%
    mutate(bid_value = as.integer(gsub("[^0-9]+", "", response)))%>%
  select(-num_stimuli)

```

Now I'm going to distribute the bid value to its corresponding block for each df. I will also record which block each group of trials is, remove unnecessary columns, and change the datatypes of necessary columns (i.e. subject id).
``` {r data_wrangling}
# spread bid and blocks completed value onto the entire block
# this new column will be how much the participant bid 

sr_practice_num <- 8
sr_per_block <- 10
vs_practice_num <- 16
vs_per_block <- 20
num_blocks <- 13

# Helper function to add a survey-text row if missing
add_survey_text_row <- function(df) {
  if (nrow(df) > 0 && df$trial_type[1] != "survey-text") {
    new_row <- tibble(
      blocks_completed = '0',
      trial_type = 'survey-text',
      run_id = as.character(df$run_id[1]),
      trial_index = '-1'
    )
    df <- bind_rows(new_row, df)
  }
  return(df)
}

# Function to process data
process_data <- function(data, per_block) {
  data %>%
    nest(data = everything()) %>%
    mutate(data = map(data, add_survey_text_row)) %>%
    unnest(cols = data) %>%
    mutate(
      switch_next_block = ifelse(switch_next_block == "", NA, switch_next_block),
      group = rep(1:(n() %/% (per_block + 1) + 1), each = (per_block + 1), length.out = n())
    ) %>%
    group_by(group) %>%
    mutate(switch_next_block = as.character(switch_next_block)) %>%
    fill(bid_value, switch_next_block, blocks_completed, .direction = "down") %>%
    ungroup() %>%
    select(-group, -bonus, -overall_accuracy, -score_pc, -score_ls)
}

# Spatial Recall
sr <- df_all_cleaned %>%
  filter(
    (prevBlockType == "spatial_recall" & switch_next_block == "false") |
      (prevBlockType == "vs" & switch_next_block == "true") |
      (game_type == "spatial_recall")
  ) %>%
  group_by(run_id)

sr_final <- sr %>%
  group_split(run_id) %>%
  map_df(~ process_data(.x, sr_per_block))

# Visual Search
vs <- df_all_cleaned %>%
  filter(
    (prevBlockType == "spatial_recall" & switch_next_block == "true") |
      (prevBlockType == "vs" & switch_next_block == "false") |
      (game_type == "vs")
  ) %>%
  group_by(run_id)

vs_final <- vs %>%
  group_split(run_id) %>%
  map_df(~ process_data(.x, vs_per_block))

# Combine them all
final_df <- bind_rows(sr_final, vs_final) %>%
  mutate(subj_id = as.numeric(run_id), blocks_completed = as.numeric(blocks_completed,na.RM = TRUE)) %>%
  select(-run_id,-generated_BDM_value,-question_order) %>%
  mutate(curr_block_num = blocks_completed + 1) 
```

``` {r data_wrangling}
total_data <- final_df %>%
  arrange(subj_id, curr_block_num) %>%
  rename(preceding_bid = bid_value)

bid_vals <- total_data %>%
  filter(trial_type == "survey-text") %>%
  group_by(subj_id) %>%
  arrange(subj_id,blocks_completed) %>%
  mutate(following_bid = lead(preceding_bid))

total_data <- total_data %>%
  left_join(bid_vals %>% select(subj_id, curr_block_num, following_bid),
            by = c("subj_id","curr_block_num"))


# get average bids per participant
avg_subj_bids <- total_data %>%
  filter(trial_type == "survey-text") %>%
  group_by(subj_id) %>%
  summarise(avg_bids = mean(preceding_bid,na.rm = TRUE),stdev_bids = sd(preceding_bid, na.rm = TRUE)) %>%
  ungroup()
total_data <- total_data %>%
  left_join(avg_subj_bids, by = "subj_id")

# make a column that represents how different (in stdev) the amount they want to switch is from their mean
total_data <- total_data %>%
  mutate(preceding_bid_z_score = if_else(stdev_bids == 0, 0, 
                                         ifelse(is.na(preceding_bid),0,
                                                ((preceding_bid - avg_bids) / 
                                                   stdev_bids))),
         following_bid_z_score = if_else(stdev_bids == 0, 0, 
                                         ifelse(is.na(following_bid),0,
                                                ((following_bid - avg_bids) / stdev_bids)))) %>%
  filter(trial_type != "survey-text") %>%
  select(-time_elapsed,-response,-sequence, -trial_id, -choices, -ITIParams,-correct_response, -missed_response,-backwards,-responses,-practice,-prevBlockType,
         -preceding_bid,-following_bid,-avg_bids,-stdev_bids) %>%
  rename(block_switched=switch_next_block)

# Now I will calculate average accuracy per block.
# conversion dict leftover
conversion <- c("true" = 1, "false" = 0)

avg_spatial_recall <- total_data %>%
  filter(game_type == "spatial_recall") %>%
  group_by(subj_id, curr_block_num) %>%
  summarise(avg_accuracy = mean(as.numeric(score_an), na.rm = TRUE),stdev_accuracy = sd(as.numeric(score_an),na.rm = TRUE))%>%
  arrange(subj_id,curr_block_num)

avg_vs <- total_data %>%
  filter(game_type == "vs") %>%
  group_by(subj_id, curr_block_num) %>%
  summarise(avg_accuracy = mean(as.numeric(correct_trial), na.rm = TRUE),stdev_accuracy = sd(as.numeric(correct_trial),na.rm=TRUE))

avg_per_block <- bind_rows(avg_spatial_recall, avg_vs) %>%
  arrange(subj_id, curr_block_num)

total_data <- total_data %>%
  left_join(avg_per_block, by = c("subj_id","curr_block_num"))

```

**basic analysis and plots of the data**

Plotting bids over time:
``` {r data_wrangling}
bid_block_total <- total_data %>%
  select(subj_id,curr_block_num,blocks_completed,following_bid_z_score,
         preceding_bid_z_score,avg_accuracy,stdev_accuracy) %>%
  group_by(subj_id,curr_block_num,blocks_completed,avg_accuracy,stdev_accuracy) %>%
  summarise(avg_following_bid_z = mean(following_bid_z_score),
            avg_preceding_bid_z = mean(preceding_bid_z_score))

# faceted by subject
bid_block_total %>%
  mutate(subj_id = as.factor(subj_id)) %>%
  ggplot(mapping = aes(x=curr_block_num,y=avg_following_bid_z,fill=subj_id,color=subj_id)) +
  geom_point(alpha = 0.3,
             position = position_jitter(height = 0, width = 0.1)) +
  facet_wrap(~subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  labs(x = "Block number", 
       y = "Z-scored bid offer (relative to each subject's avg and sd)", 
       title = "Bid offers following each block, by subject")

# not faceted by subject
bid_block_total %>%
  mutate(subj_id = as.factor(subj_id)) %>%
  group_by(curr_block_num) %>%
  ggplot(mapping = aes(x=curr_block_num,y=avg_following_bid_z,fill=subj_id,color=subj_id)) +
  geom_point(alpha = 0.3,
             position = position_jitter(height = 0, width = 0.1)) +
  geom_smooth(method="lm",se=TRUE) +
  labs(x = "Block number", 
       y = "Z-scored bid offer (relative to each subject's avg and sd)", 
       title = "Bid offers following each block, by subject")

# averaged across all participants
bid_block_total %>%
  group_by(curr_block_num) %>%
  ggplot(mapping = aes(x=curr_block_num,y=avg_following_bid_z)) +
  geom_point(alpha = 0.3,
             position = position_jitter(height = 0, width = 0.1)) +
  geom_smooth(method="lm",se=TRUE) +
  labs(x = "Block number", 
       y = "Z-scored bid offer (relative to each subject's avg and sd)", 
       title = "Bid offers following each block, all subjects all blocks")
```

Plotting preceding bid by avg accuracy in following block:
``` {r data_wrangling}
# including all subjects
bid_block_total %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x = avg_preceding_bid_z, y = avg_accuracy)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 3) +  # Points colored by block number
  labs(x = "Bid Z-Score",
       y = "Average Accuracy in Following Block",
       color = "Block Number") +
  ggtitle("Bid Z-Score by Following Average Accuracy for Each Block, across subjects")

# faceted by subjects
bid_block_total %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x = avg_preceding_bid_z, y = avg_accuracy)) +
  facet_wrap(~subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 3) +  # Points colored by block number
  labs(x = "Preceding Bid Z-Score",
       y = "Average Accuracy",
       color = "Block Number") +
  ggtitle("Bid Z-Score by Following Average Accuracy for Each Block,by subject")
```

Plotting following bid by avg accuracy in a block:
``` {r data_wrangling}
# including all subjects
bid_block_total %>%
  ggplot(mapping = aes(x = avg_following_bid_z, y = avg_z_accuracy)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 3) +  # Points colored by block number
  labs(x = "Following Bid Z-Score",
       y = "Average Z-scored Accuracy",
       color = "Block Number") +
  ggtitle("Average Accuracy by Following Bid Z-Score for Each Block, across subjects")

# faceted by subjects
bid_block_total %>%
  ggplot(mapping = aes(x = avg_following_bid_z, y = avg_accuracy)) +
  facet_wrap(~subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 3) +  # Points colored by block number
  labs(x = "Following Bid Z-Score",
       y = "Average Accuracy",
       color = "Block Number") +
  ggtitle("Average Accuracy by Following Bid Z-Score for Each Block, by subject")

```


``` {r data_wrangling}
conversion_switch <- c("true" = 1, "false" = 0)
bid_block_total_details <- total_data %>%
  select(subj_id,curr_block_num,blocks_completed,following_bid_z_score,
         preceding_bid_z_score,avg_accuracy,stdev_accuracy,game_type,block_switched) %>%
  group_by(subj_id,curr_block_num,blocks_completed,avg_accuracy,stdev_accuracy,block_switched,game_type) %>%
  summarise(avg_following_bid_z = mean(following_bid_z_score),
            avg_preceding_bid_z = mean(preceding_bid_z_score)) %>%
  mutate(block_switched = ifelse(is.na(block_switched),0,conversion_switch[block_switched])) %>%
  arrange(subj_id, curr_block_num)
```
``` {r data_wrangling}
total_data %>%
  filter(game_type == "spatial_recall") %>%
  mutate(subj_id = as.factor(subj_id),score_an = as.numeric(score_an)) %>%
  arrange(trial_index) %>%
  ggplot(mapping = aes(x = curr_block_num,y=score_an,fill=subj_id,color=subj_id)) +
  facet_wrap(~subj_id,ncol=2) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(alpha = 0.4,
             position = position_jitter(width = 0.3,
                                        height = 0),
             size = 2) +
  labs(x = "Block number (arranged by trial_index)",
       y = "Accuracy per trial") +
  ggtitle("Spatial Recall: Accuracy over trials, by subject")

total_data %>%
  filter(game_type == "vs") %>%
  mutate(subj_id = as.factor(subj_id),correct = as.numeric(correct_trial)) %>%
  arrange(trial_index) %>%
  ggplot(mapping = aes(x = curr_block_num,y=correct,fill=subj_id,color=subj_id)) +
  facet_wrap(~subj_id,ncol=2) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(alpha = 0.4,
             position = position_jitter(width = 0.3,
                                        height = 0),
             size = 2) +
  labs(x = "Block number (arranged by trial_index)",
       y = "Accuracy per trial") +
  ggtitle("VS: Accuracy over trials, by subject")

```

``` {r data_wrangling}
bid_block_total_details %>%
  filter(game_type == "vs") %>%
  mutate(subj_id = as.factor(subj_id)) %>%
  group_by(curr_block_num) %>%
  ggplot(mapping = aes(x = curr_block_num, y = avg_accuracy)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = subj_id), size = 3) +  # Points colored by block number
  labs(x = "Block number",
       y = "Average Accuracy") +
  ggtitle("VS: Average Accuracy for Each Block, across subjects")

bid_block_total_details %>%
  filter(game_type == "spatial_recall") %>%
  mutate(subj_id = as.factor(subj_id)) %>%
  group_by(curr_block_num) %>%
  ggplot(mapping = aes(x = curr_block_num, y = avg_accuracy)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = subj_id), size = 3) +  # Points colored by block number
  labs(x = "Block number",
       y = "Average Accuracy") +
  ggtitle("Spatial Recall: Average Accuracy for Each Block, across subjects")
```



By subject:

``` {r data_wrangling}
bid_block_total_details %>%
  filter(game_type == "vs") %>%
  mutate(subj_id = as.factor(subj_id)) %>%
  group_by(curr_block_num) %>%
  ggplot(mapping = aes(x = curr_block_num, y = avg_accuracy)) +
  facet_wrap(~subj_id) + 
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = subj_id), size = 3) +  # Points colored by block number
  labs(x = "Block number",
       y = "Average Accuracy") +
  ggtitle("VS: Average Accuracy for Each Block, by subjects")

bid_block_total_details %>%
  filter(game_type == "spatial_recall") %>%
  mutate(subj_id = as.factor(subj_id)) %>%
  group_by(curr_block_num) %>%
  ggplot(mapping = aes(x = curr_block_num, y = avg_accuracy)) +
  facet_wrap(~subj_id) + 
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = subj_id), size = 3) +  # Points colored by block number
  labs(x = "Block number",
       y = "Average Accuracy") +
  ggtitle("Spatial Recall: Average Accuracy for Each Block, by subjects")
```




Looking at overall average accuracy in spatial recall vs in vs, by subject
``` {r data_wrangling}
total_data %>%
  mutate(subj_id = as.factor(subj_id),score_an = as.numeric(score_an),
         correct = conversion_switch[correct]) %>%
  mutate(correct_total = ifelse(game_type == "spatial_recall",score_an,as.numeric(correct_trial)),
         block_switched = ifelse(is.na(block_switched),"block did not switch", ifelse(block_switched == 0,"block did not switch","block switched"))) %>%
  group_by(subj_id) %>%
  ggplot(mapping = aes(x=game_type,y=correct_total)) +
  facet_wrap(~block_switched) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.4,
                                        height = 0.01)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1) +
  labs(x="task type",y="accuracy per trial per subject")+
  ggtitle("Trial accuracy by task type")

bid_block_total_details %>%
  mutate(subj_id = as.factor(subj_id),block_switched = ifelse(is.na(block_switched),"block did not switch", ifelse(block_switched == 0,"block did not switch","block switched"))) %>%
  ggplot(mapping = aes(x=game_type,y=avg_accuracy,color=subj_id)) +
  facet_wrap(~block_switched) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.4,
                                        height = 0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1) +
  labs(x="task type",y="average accuracy per block per subject")+
  ggtitle("Block accuracy by task type, across subjects")

bid_block_total_details %>%
  mutate(subj_id = as.factor(subj_id),block_switched = ifelse(is.na(block_switched),"block did not switch", ifelse(block_switched == 0,"block did not switch","block switched"))) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_accuracy,color=subj_id)) +
  facet_wrap(~game_type) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.4,
                                        height = 0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1) +
  labs(x="Is this a switched task",y="average accuracy per block per subject")+
  ggtitle("Block accuracy by task type, across subjects")
```

Bid offers by switch or not
``` {r data_wrangling}
bid_block_total_details %>%
  mutate(subj_id = as.factor(subj_id),block_switched = ifelse(is.na(block_switched),"block did not switch", ifelse(block_switched == 0,"block did not switch","block switched"))) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_following_bid_z,color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  facet_wrap(~game_type)+
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  labs(x="Did the task switch this block?",y="Average bid by participant/block after this block")+
  ggtitle("Relationship between switch status and following bid offer")

```

Do mixed effects models/more plots to test and look at:
- does bid offer predict future accuracy
- if bid offer is in higher bucket, and switch was successful vs unsucessful, how does that change accuracy? (accounting for game type)
- does successful switching predict future accuracy
- does accuracy predict bid offer
- how does all of this differ by game_type
``` {r data_wrangling}
# to try to visualize this question: if bid offer is in higher bucket, and switch was successful vs unsucessful, how does that change accuracy? (accounting for game type)
breaks <- c(-Inf, -1, 0, 1, Inf)
labels <- c('more than 1 sd below', '0 to 1 sd below', '0 to 1 sd above', 'more than 1 sd above')

bid_block_total_details_binned <- bid_block_total_details %>%
  mutate(bid_bin_preceding = cut(avg_preceding_bid_z, breaks = breaks, labels = labels, right = FALSE),
         bid_bin_following = cut(avg_following_bid_z, breaks = breaks, labels = labels, right = FALSE))%>%
  mutate(subj_id = as.factor(subj_id),block_switched = ifelse(is.na(block_switched),"block did not switch", ifelse(block_switched == 0,"switch","no switch"))) %>%
  mutate(subj_id = as.factor(subj_id))

bid_block_total_details_binned %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_accuracy,color=subj_id)) +
  facet_wrap(~bid_bin_preceding,ncol=4) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.5,position = position_jitter(width=0.2,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="Average accuracy in this block")+
  ggtitle("Relationship between bid offer, switch status and following average accuracy")
```


``` {r data_wrangling}
bid_block_total_details_binned %>%
  group_by(block_switched) %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x=avg_preceding_bid_z,y=avg_accuracy, color = block_switched)) +
  geom_point(alpha = 0.5)+
  geom_smooth(method="lm",se=TRUE)
```


calculating overall averages per task: 
``` {r data_wrangling}
all_avgs <- total_data %>%
  mutate(correct_val = ifelse(game_type == "vs",as.numeric(correct_trial),as.numeric(score_an))) %>%
  select(subj_id,game_type, correct_val) %>%
  group_by(subj_id,game_type) %>%
  summarize(overall_game_avg = mean(correct_val))

all_avgs %>%
  ggplot(mapping = aes(x=game_type, y=overall_game_avg)) +
  geom_point(aes(x=game_type, y=overall_game_avg)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game Type",y="Average accuracy on all trials of this game, per subject")+
  ggtitle("Average of subject mean performance on each game")

```


**Look at some of this stuff, after excluding participants who never switched**

Exclude participants who never switched:
``` {r data_wrangling}
subjects_no_spatial_recall <- total_data %>%
  group_by(subj_id) %>%
  summarize(has_spatial_recall = any(game_type == "spatial_recall")) %>%
  filter(!has_spatial_recall) 

subjects_no_vs <- total_data %>%
  group_by(subj_id) %>%
  summarize(has_vs = any(game_type == "vs")) %>%
  filter(!has_vs) 

head(subjects_no_spatial_recall)
head(subjects_no_vs)

excluded_switch_data <- total_data %>%
  anti_join(subjects_no_spatial_recall, by = "subj_id") %>% 
  anti_join(subjects_no_vs, by = "subj_id")

subjects_no_spatial_recall$subj_id <- as.factor(subjects_no_spatial_recall$subj_id)
subjects_no_vs$subj_id <- as.factor(subjects_no_vs$subj_id)

excluded_bid_block_total_details_binned <- bid_block_total_details_binned %>%
  anti_join(subjects_no_spatial_recall, by = "subj_id") %>% 
  anti_join(subjects_no_vs, by = "subj_id") 
```

Exclude participants who got above 98% in both games
``` {r data_wrangling}
cutoff = 0.97

total_data <- total_data %>%
  ungroup() %>%
  mutate(correct_val = ifelse(game_type == "vs",as.numeric(correct_trial),as.numeric(score_an))) 

avgs <- total_data %>%
  select(subj_id,game_type, correct_val) %>%
  group_by(subj_id,game_type) %>%
  summarize(overall_game_avg = mean(correct_val))

subjects_high_accuracy <- avgs %>%
  summarize(min_avg_score = min(overall_game_avg)) %>%
  filter(min_avg_score > cutoff)

excluded_switch_data <- total_data %>%
  anti_join(subjects_high_accuracy, by = "subj_id")

subjects_high_accuracy$subj_id <- as.factor(subjects_high_accuracy$subj_id)
excluded_bid_block_total_details_binned <- excluded_bid_block_total_details_binned %>%
  anti_join(subjects_high_accuracy, by = "subj_id")

```


``` {r data_wrangling}
excluded_bid_block_total_details_binned %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_accuracy,color=subj_id)) +
  facet_wrap(~bid_bin_preceding,ncol=4) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.5,position = position_jitter(width=0.2,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="Average accuracy in this block")+
  ggtitle("Relationship between bid offer, switch status and following average accuracy")
```






