This is the analysis on the really early pilot data for the spatial recall and
go / no-go task. (Link here: https://duprbgais2.cognition.run)

The goal of this pre-pilot was just to see how people perform on the go/no-go
and spatial recall task (i.e. is one a lot harder, is one a lot easier) and also
to check if people do make more errors as difficulty increases

```{r libraries}
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse

# set the default ggplot theme 
theme_set(theme_classic())
```

**reading in the data**
``` {r data_wrangling}
setwd("../../data/pre_pilot_A/")

csv_files <- list.files(pattern = "\\.csv$")

# Function to read a CSV file and convert all columns to character type
read_csv_as_character <- function(file) {
  df <- read.csv(file, stringsAsFactors = FALSE)
  df[] <- lapply(df, as.character)
  return(df)
}

# Read each CSV file, ensuring all data is read as character, and combine them
combined_df <- bind_rows(lapply(csv_files, read_csv_as_character))

head(combined_df)
```

**pre-processing the data**
```{r pre_process}
# take out ip info etc
anonymized_data_full <- combined_df %>%
  select(-recorded_at,-ip,-user_agent,-referer,-fbclid,-sequence_length,
         -accept_language,-device,-internal_node_id,-view_history)

# take out browser info (maybe bring this back in later if I want to look at
# different browser impact)
# also take out source code version (they are all the same but can add 
# verification later)
# also take out screen information
anonymized_data_full <- anonymized_data_full %>%
  select(-source_code_version, -contains("browser"),-contains("platform"),
         -contains("screen"),-contains("width"),-contains("height"),
         -contains("failed"),-condition)

# add task_type labels (either "sr" or gng")
# remove instruction trials, and fixation trials from "sr"
relevant_full <- anonymized_data_full %>%
  filter(trial_type != "instructions", !grepl("screen", trial_type, ignore.case = TRUE)) %>%
  select(-event_history) %>%
  mutate(task_type = ifelse(grepl("^\\[.*\\]$", sequence),"sr",ifelse(task=="response","gng",ifelse(task=="fixation","gng_fix",NA))))

## keep only sr, gng trials
## for each gng trial, add the following fixation length as a column called
# round_fix_len
# score_pc is number /4 that are in the correct position
# score_Ic is number / 4 of integers that are correct (indep. of position)
trial_full <- relevant_full %>%
  mutate(next_fixation_length = ifelse(lag(task_type) == "gng", fixation_time, NA)) %>%
  mutate(next_fixation_length = lead(next_fixation_length)) %>%
  mutate(round_fix_len = ifelse(task_type == "gng", next_fixation_length, NA)) %>%
  select(-next_fixation_length) %>%
  filter(task_type == "gng" | task_type == "sr") %>%
  mutate(correct_bool = as.numeric(score_an)) %>%
  mutate(correct_bool = ifelse(task_type=="gng",ifelse(correct=="true",1,0),correct_bool),run_id=as.numeric(run_id),score_pc = as.numeric(score_pc,na.RM=T)/4,tile_duration=as.numeric(tile_duration,na.RM=T),round_fix_len = as.numeric(round_fix_len,na.RM=T), rt= as.numeric(rt,na.RM=T),trial_index=as.numeric(trial_index,na.RM=T))  %>%
  select(subject_id = run_id,task_type,correct_bool,sr_perc_corr = score_pc, sr_tile_duration = tile_duration,gng_corr_response = correct_response,gng_fix_len = round_fix_len,rt,trial_index)
```
**Spatial recall trial analysis**
```{r sr_analysis}
trial_full %>%
  mutate(subject_id = as.factor(subject_id)) %>%
  filter(task_type=="sr") %>%
  ggplot(mapping=aes(x=trial_index,y=sr_perc_corr,color=subject_id,fill=subject_id)) +
  facet_wrap(~subject_id) +
  geom_point() +
  labs(y="percent accuracy",title="4 square spatial recall accuracy by trial number")
```
```{r sr_analysis}
trial_full %>%
  mutate(subject_id = as.factor(subject_id)) %>%
  filter(task_type=="sr") %>%
  ggplot(mapping=aes(x=sr_tile_duration,y=sr_perc_corr,color=subject_id,fill=subject_id)) +
  facet_wrap(~subject_id) +
  geom_point() +
  labs(y="percent accuracy",x="flash tile duration", title="4 square spatial recall accuracy by tile duration")
```

**GNG trial analysis**
```{r gng_analysis}
trial_full %>%
  mutate(subject_id = as.factor(subject_id)) %>%
  filter(task_type=="gng") %>%
  ggplot(mapping=aes(x=trial_index,y=correct_bool,color=subject_id,fill=subject_id)) +
  facet_wrap(~subject_id) +
  geom_point() +
  labs(y="accuracy",title="go no go accuracy by trial number")
```
```{r gng_analysis}
trial_full %>%
  mutate(subject_id = as.factor(subject_id)) %>%
  filter(task_type=="gng") %>%
  ggplot(mapping=aes(x=gng_fix_len,y=correct_bool,color=subject_id,fill=subject_id)) +
  facet_wrap(~subject_id) +
  geom_point() +
  labs(y="accuracy",x="fixation (break) length", title="go no go accuracy by fixation length")
```
**gen info:**
```{r trial_info}
trial_full %>%
  group_by(subject_id,task_type) %>%
  summarize(count = n())
```