---
title: "pilotD_second_analysis"
output: html_document
date: "2024-07-26"
---
This is the updated analysis on the "pilot D second" and "pilot D second ProlificCopy" participants. These are prolific participants after I made the visual search more difficult following pilot D.

In this analysis, I z-scored the participant performance within each task in order to better compare across the two tasks. 
The spatial recall was 4 squares at a time, and the visual search was conjunction only and 24 items only. 

The setup was:
5 spatial recall practice
15 visual search practice

20 blocks
- 30 visual search per block
- 12 spatial recall per block

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
##library(jsonlite)
library("broom")      # for tidying up linear models 
library("car")        # for running ANOVAs
library("afex")       # also for running ANOVAs
library("emmeans")    # for calculating constrasts

# set the default ggplot theme 
theme_set(theme_classic())
```

**reading in the data**
``` {r data_wrangling}
setwd("../../data/pilotD_second/prolific_original")

csv_files <- list.files(pattern = "\\.csv$")

# Function to read a CSV file and convert all columns to character type
read_csv_as_character <- function(file) {
  df <- read.csv(file, stringsAsFactors = FALSE)
  df[] <- lapply(df, as.character)
  return(df)
}

df_all <- bind_rows(lapply(csv_files,read_csv_as_character))
```
Now we need to read in the data from the ProlificCopy cognition.run, and modify the run_ids (since there may be some run_id repeats between the two data folders)
``` {r data_wrangling}
setwd("../../data/pilotD_second/prolific_copy")

csv_files <- list.files(pattern = "\\.csv$")

# Function to read a CSV file and convert all columns to character type
read_csv_as_character <- function(file) {
  df <- read.csv(file, stringsAsFactors = FALSE)
  df[] <- lapply(df, as.character)
  return(df)
}

df_all_prolific_copy <- bind_rows(lapply(csv_files,read_csv_as_character))

df_all_prolific_copy <- df_all_prolific_copy %>%
  mutate(run_id = as.character((as.integer(run_id) + 500)))

df_all <- bind_rows(df_all, df_all_prolific_copy)
```
**pre-processing the data**
First I will anonymize the data and remove unneccesary columns:
``` {r data_wrangling_anon}
anonymize_clean <- function(df) {
  df <- df %>%
    select(-recorded_at,-url,-ip,-user_agent,-referer,-sequence_length,
         -accept_language,-device,-internal_node_id,-view_history,
         -source_code_version, -contains("browser"),-contains("platform"),
         -contains("screen"),-contains("width"),-contains("height"),
         -contains("failed"),-condition,-success,-event_history)
  return(df)
}
df_all <- anonymize_clean(df_all)
```

Now I will take out the practice trials and save them to a different df, I will also remove practice and all other trial types (other than sr or vs) from my dataframe. I will also give df_all a column for participant ratings of difficulty and boringness, as well as their practice accuracy results
``` {r data_wrangling_add_cols}
# save practice to practice_runs_df
practice_runs_df <- df_all %>%
  filter(practice == "true")

# save feedback to a df
# make a column for how much they rated vs and sr difficulty and boringness
feedback_df <- df_all %>%
  filter(trial_type == "survey-text") %>%
  filter(str_detect(response, "bid_decision") | str_detect(response, "game_description") | str_detect(response, "boring") | str_detect(response, "prolific_id"))

feedback_df <- feedback_df %>%
  mutate(response = map(response, ~ jsonlite::fromJSON(.))) %>%
  unnest_wider(response)

feedback_temp_sr <- feedback_df %>%
  filter(!is.na(sr_boring)) %>%
  select(run_id, sr_boring, sr_difficult)
feedback_temp_vs <- feedback_df %>%
  filter(!is.na(vs_boring)) %>%
  select(run_id, vs_boring, vs_difficult)
prolific_ids_df <- feedback_df %>%
  filter(!is.na(prolific_id)) %>%
  select(run_id, prolific_id)

df_all <- df_all %>%
  left_join(feedback_temp_sr, by = "run_id") %>%
  left_join(feedback_temp_vs, by = "run_id") %>%
  left_join(prolific_ids_df, by = "run_id")

# make a column for average practice score per participant and put it into the main df
temp <- practice_runs_df %>%
  select(run_id, trial_type, score_an, correct_trial) %>%
  mutate(correct = ifelse(trial_type == "spatial-recall",as.integer(score_an),ifelse(correct_trial=="null",0,as.integer(correct_trial)))) %>%
  select(run_id, trial_type, correct) %>%
  group_by(run_id, trial_type) %>%
  summarise(avg_correct = mean(correct)) %>%
  mutate(sr_practice_accuracy = ifelse(trial_type == "spatial-recall",avg_correct,NA),vs_practice_accuracy = ifelse(trial_type != "spatial-recall",avg_correct,NA)) %>%
  ungroup() %>%
  select(run_id, sr_practice_accuracy, vs_practice_accuracy) %>%
  group_by(run_id) %>%
  summarise(
    sr_practice_accuracy = max(sr_practice_accuracy, na.rm = TRUE),
    vs_practice_accuracy = max(vs_practice_accuracy, na.rm = TRUE)
  ) %>%
  ungroup()
df_all <- merge(df_all, temp, by = "run_id")

# remove practice & other non-task rows from df
df_all_cleaned <- df_all %>%
  filter(trial_type != "instructions", trial_type != "preload", 
           trial_type != "survey-multi-choice",
           (trial_type != 'html-keyboard-response' | trial_id =='test_trial'),
           (trial_type != 'html-button-response'),
           !grepl("screen", trial_type, ignore.case = TRUE)) %>%
    filter(practice != "true") %>%
    mutate(bid_value = as.integer(gsub("[^0-9]+", "", response)))%>%
  select(-num_stimuli)

# update correct column for all df_all_cleaned
df_all_cleaned <- df_all_cleaned %>%
  mutate(correct = ifelse(trial_type == "spatial-recall",as.integer(score_an, na.rm = TRUE),ifelse(correct_trial=="null",0,as.integer(correct_trial,na.rm=TRUE)))) %>%
  select(-score_an, -correct_trial) %>%
  ungroup()

```
Now I'm going to plot the average performance of each participant in each task (prior to z-scoring them below):
``` {r data_wrangling_bids_tasks}
copy_for_avg <- df_all_cleaned %>%
  filter(!is.na(correct))

copy_for_avg <- copy_for_avg %>%
  select(run_id, game_type, correct,trial_index) %>%
  mutate(subj_id = as.factor(run_id), trial_index = as.integer(trial_index)) %>%
  group_by(run_id, game_type) %>%
  arrange(trial_index) %>%
  mutate(trial_count = row_number()) %>%
  ungroup()

# across subjects, how accuracy changes over time per task
copy_for_avg %>%
  group_by(subj_id) %>%
  ggplot(mapping = aes(x=trial_count,y=correct)) +
  facet_wrap(~game_type) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = subj_id), size = 3) +  # Points colored by block number
  labs(x = "Trial index",
       y = "Accuracy on this trial per subject") +
  ggtitle("Spatial Recall: Average Accuracy Over Time, across subjects")


# average of all subj averages
copy_for_avg %>%
  group_by(subj_id, game_type) %>%
  summarise(avg_correct = mean(correct)) %>%
  ggplot(mapping = aes(x=game_type,y=avg_correct)) +
 geom_point(alpha = 0.5,position = position_jitter(width = 0.4,
                              height = 0.01)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game Type",y="Average accuracy on all trials of this game, per subject")+
  ggtitle("Average of subject mean performance on each game (pre-exclusion)")

copy_for_avg %>%
  group_by(subj_id, game_type) %>%
  summarise(avg_correct = mean(correct)) %>%
  ggplot(mapping = aes(x=game_type,y=avg_correct)) +
 geom_point(alpha = 0.5,position = position_jitter(width = 0.4,
                              height = 0.01)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = median, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game Type",y="Average accuracy on all trials of this game, per subject")+
  ggtitle("Median of subject average mean performance on each game (pre-exclusion)")
```
Now I'm going to distribute the bid value to its corresponding block for each df. I will also record which block each group of trials is, remove unnecessary columns, and change the datatypes of necessary columns (i.e. subject id). I will also save the overall average and sd of each participant for each task. #TODO (should I do this overall, or per block?) For now overall.

``` {r data_wrangling_bids_tasks}
# spread bid and blocks completed value onto the entire block
# this new column will be how much the participant bid 

sr_practice_num <- 5
sr_per_block <- 12
vs_practice_num <- 15
vs_per_block <- 30
num_blocks <- 20

# Helper function to add a survey-text row if missing
add_survey_text_row <- function(df) {
  if (nrow(df) > 0 && df$trial_type[1] != "survey-text") {
    new_row <- tibble(
      blocks_completed = '0',
      switch_next_block = 'false',
      trial_type = 'survey-text',
      run_id = as.character(df$run_id[1]),
      trial_index = '-1'
    )
    df <- bind_rows(new_row, df)
  }
  return(df)
}

# Function to process data
process_data <- function(data, per_block) {
  data %>%
    nest(data = everything()) %>%
    mutate(data = map(data, add_survey_text_row)) %>%
    unnest(cols = data) %>%
    mutate(
      switch_next_block = ifelse(switch_next_block == "", NA, switch_next_block),
      group = rep(1:(n() %/% (per_block + 1) + 1), each = (per_block + 1), length.out = n())
    ) %>%
    group_by(group) %>%
    mutate(switch_next_block = as.character(switch_next_block)) %>%
    fill(bid_value, switch_next_block, blocks_completed, .direction = "down") %>%
    ungroup() %>%
    select(-group, -bonus, -overall_accuracy, -score_pc, -score_ls, correct)
}
```

``` {r data_wrangling_bids_tasks}
# Spatial Recall
sr_final <- df_all_cleaned %>%
  filter(
    (prevBlockType == "spatial_recall" & switch_next_block == "false") |
      (prevBlockType == "vs" & switch_next_block == "true") |
      (game_type == "spatial_recall")
  ) %>%
  group_by(run_id)

sr_final <- sr_final %>%
  group_split(run_id) %>%
  map_df(~ process_data(.x, sr_per_block))%>%
  mutate(rt_num = as.numeric(rt, na.rm = TRUE))

# Visual Search
vs_final <- df_all_cleaned %>%
  filter(
    (prevBlockType == "spatial_recall" & switch_next_block == "true") |
      (prevBlockType == "vs" & switch_next_block == "false") |
      (game_type == "vs")
  ) %>%
  group_by(run_id)

vs_final <- vs_final %>%
  group_split(run_id) %>%
  map_df(~ process_data(.x, vs_per_block)) %>%
  mutate(rt_num = as.numeric(rt, na.rm = TRUE))
```

``` {r data_wrangling_bids_tasks}
# For each participant for each task, calc average and sd of performance across blocks and of rt
temp <- sr_final %>%
  group_by(run_id) %>%
  filter(trial_type == "spatial-recall") %>%
  summarize(avg_sr_correct = mean(correct, na.rm = TRUE), sd_sr_correct = sd(correct,na.rm = TRUE), avg_sr_rt = mean(rt_num, na.rm=TRUE), sd_sr_rt = sd(rt_num, na.rm=TRUE)) %>%
  ungroup()

sr_final <- merge(sr_final, temp, by = "run_id") %>%
  mutate(z_accuracy_sr = ifelse(sd_sr_correct != 0, ((correct - avg_sr_correct)/sd_sr_correct), 0), z_rt_sr = ifelse(sd_sr_rt != 0, ((rt_num - avg_sr_rt)/sd_sr_rt),0))

temp <- vs_final %>%
  group_by(run_id) %>%
  filter(trial_id == "test_trial") %>%
  summarize(avg_vs_correct = mean(correct, na.rm = TRUE), sd_vs_correct = sd(correct,na.rm = TRUE), avg_vs_rt = mean(rt_num, na.rm=TRUE), sd_vs_rt = sd(rt_num, na.rm=TRUE)) %>%
  ungroup()

vs_final <- merge(vs_final, temp, by = "run_id") %>%
  mutate(z_accuracy_vs = ifelse(sd_vs_correct != 0, ((correct - avg_vs_correct)/sd_vs_correct), 0), z_rt_vs = ifelse(sd_vs_rt != 0, ((rt_num - avg_vs_rt)/sd_vs_rt),0))
  

# Combine them all
final_df <- bind_rows(sr_final, vs_final) %>%
  mutate(subj_id = as.numeric(run_id), blocks_completed = as.numeric(blocks_completed,na.RM = TRUE)) %>%
  select(-run_id,-generated_BDM_value,-question_order) %>%
  mutate(curr_block_num = blocks_completed + 1)

final_df <- final_df %>%
  group_by(subj_id, game_type) %>%
  arrange(subj_id,blocks_completed)
```

``` {r data_wrangling_bids_tasks}
# Clean out columns we don't need anymore
# CAN USE sd_avg_data LATER TO ADD THESE DETAILS BACK IN
extra_data_for_model <- final_df %>%
  select(subj_id, game_type, avg_vs_correct, avg_sr_correct, avg_vs_rt, avg_sr_rt, sd_vs_correct, sd_sr_correct, sd_sr_correct, sd_vs_correct, sr_practice_accuracy, vs_practice_accuracy, sr_boring, sr_difficult, vs_boring, vs_difficult, missed_response, sequence, backwards, responses, missed_response, stimulus, time_elapsed, rt, trial_id, trial_duration, stimulus_duration, target_present, correct_response, order_and_color_of_rectangles, target_rectangle_location, ITIParams, numberStim, sd_vs_rt, sd_sr_rt, sr_accuracy, vs_accuracy, choices, exp_stage, prolific_id)

final_df <- final_df %>%
  select(-c(avg_vs_correct, avg_sr_correct, avg_vs_rt, avg_sr_rt, sd_vs_correct, sd_sr_correct, sd_sr_correct, sd_vs_correct, sr_practice_accuracy, vs_practice_accuracy, sr_boring, sr_difficult, vs_boring, vs_difficult, missed_response, sequence, backwards, responses, missed_response, stimulus, time_elapsed, rt, trial_id, trial_duration, stimulus_duration, target_present, correct_response, order_and_color_of_rectangles, target_rectangle_location, ITIParams, numberStim, sd_vs_rt, sd_sr_rt, sr_accuracy, vs_accuracy, choices, exp_stage, sr_accuracy, vs_accuracy, prolific_id))
```

Now I will z score the participant bids too. 
``` {r data_wrangling_bids_tasks}
final_df <- final_df %>%
  arrange(subj_id, curr_block_num) %>%
  rename(preceding_bid = bid_value)

bid_vals <- final_df %>%
  filter(trial_type == "survey-text") %>%
  group_by(subj_id) %>%
  arrange(subj_id,blocks_completed) %>%
  mutate(following_bid = lead(preceding_bid)) %>%
  ungroup()

final_df <- final_df %>%
  left_join(bid_vals %>% select(subj_id, curr_block_num, following_bid),
            by = c("subj_id","curr_block_num"))

# get average bids per participant
temp <- final_df %>%
  filter(trial_type == "survey-text") %>%
  group_by(subj_id) %>%
  summarise(avg_bids = mean(preceding_bid,na.rm = TRUE),stdev_bids = sd(preceding_bid, na.rm = TRUE)) %>%
  ungroup()
final_df <- final_df %>%
  left_join(temp, by = "subj_id")

# make a column that represents how different (in stdev) the amount they want to switch is from their mean
final_df <- final_df %>%
  mutate(preceding_bid_z_score = if_else(stdev_bids == 0, 0, 
                                         ifelse(is.na(preceding_bid),0,
                                                ((preceding_bid - avg_bids) / 
                                                   stdev_bids))),
         following_bid_z_score = if_else(stdev_bids == 0, 0, 
                                         ifelse(is.na(following_bid),0,
                                                ((following_bid - avg_bids) / stdev_bids)))) %>%
  filter(trial_type != "survey-text") %>%
  select(-prevBlockType,-preceding_bid,-following_bid,-avg_bids,-stdev_bids) %>%
  rename(block_switched=switch_next_block) %>%
  mutate(z_accuracy = ifelse(game_type == "vs",z_accuracy_vs,z_accuracy_sr), z_rt = ifelse(game_type == "vs",z_rt_vs,z_rt_sr)) %>%
  select(-z_accuracy_sr, -z_accuracy_vs, -z_rt_sr, -z_rt_vs)
```
AT THIS POINT:
- final_df has the z_scored bid values, z_scored accuracy per task, and z_scored rt per task. Each z-score is participant specific. 

``` {r data_wrangling_bids_tasks}
# Now I will calculate average z accuracy and z rt per block.
avg_spatial_recall <- final_df %>%
  filter(game_type == "spatial_recall") %>%
  group_by(subj_id, curr_block_num) %>%
  summarise(avg_z_accuracy = mean(z_accuracy),stdev_z_accuracy = sd(z_accuracy,na.rm = TRUE), avg_z_rt = mean(z_rt),stdev_z_rt = sd(z_rt,na.rm = TRUE))%>%
  arrange(subj_id,curr_block_num)

avg_vs <- final_df %>%
  filter(game_type == "vs") %>%
  group_by(subj_id, curr_block_num) %>%
  summarise(avg_z_accuracy = mean(z_accuracy),stdev_z_accuracy = sd(z_accuracy,na.rm = TRUE), avg_z_rt = mean(z_rt),stdev_z_rt = sd(z_rt,na.rm = TRUE))%>%
  arrange(subj_id,curr_block_num)

avg_per_block <- bind_rows(avg_spatial_recall, avg_vs) %>%
  arrange(subj_id, curr_block_num)

total_data <- final_df %>%
  left_join(avg_per_block, by = c("subj_id","curr_block_num"))
```

**PARTICIPANT EXCLUSION**
Here, we will exclude participants. We want to exclude participants who never switched. We also want to exclude participants who got over **90% accuracy** on **both** tasks or below **30% accuracy** on either task (TODO should i remove those who got over 90 on either task?)

``` {r data_wrangling}
cutoff = 0.93 # right now, to be cut out must get above this on both tasks
bottom_cutoff = 0.30 # right now, to be cut out must get below this on either task

subjects_no_switch <- total_data %>%
  group_by(subj_id) %>%
  summarize(has_spatial_recall = any(game_type == "spatial_recall"), has_vs = any(game_type == "vs")) %>%
  filter(!has_spatial_recall | !has_vs)
head(subjects_no_switch)

subjects_high_low_accuracy <- total_data %>%
  ungroup() %>%
  select(subj_id,game_type, correct) %>%
  group_by(subj_id,game_type) %>%
  summarize(overall_game_avg = mean(correct))%>%
  summarize(min_avg_score = min(overall_game_avg)) %>%
  filter(min_avg_score > cutoff | min_avg_score < bottom_cutoff)
head(subjects_high_low_accuracy)

subjects_high_low_accuracy <- subjects_high_low_accuracy %>%
  select(subj_id)
subjects_no_switch <- subjects_no_switch %>%
  select(subj_id)
excluded_participants <- bind_rows(subjects_high_low_accuracy, subjects_no_switch)
print(excluded_participants)

excluded_switch_data <- total_data %>%
  anti_join(excluded_participants, by = "subj_id") %>%
  ungroup()
```


**BASIC PLOTS**

Plotting bids over time:
``` {r data_wrangling}
bid_block_total <- excluded_switch_data %>%
  select(subj_id,curr_block_num,blocks_completed,following_bid_z_score,
         preceding_bid_z_score,avg_z_accuracy,stdev_z_accuracy, avg_z_rt, stdev_z_rt, block_switched, game_type) %>%
  group_by(subj_id,curr_block_num,blocks_completed,avg_z_accuracy,stdev_z_accuracy, avg_z_rt, stdev_z_rt, block_switched, game_type) %>%
  summarise(avg_following_bid_z = mean(following_bid_z_score),
            avg_preceding_bid_z = mean(preceding_bid_z_score))

# accuracy faceted by subject
bid_block_total %>%
  mutate(subj_id = as.factor(subj_id)) %>%
  ggplot(mapping = aes(x=curr_block_num,y=avg_following_bid_z,fill=subj_id,color=subj_id)) +
  geom_point(alpha = 0.3,
             position = position_jitter(height = 0, width = 0.1)) +
  facet_wrap(~subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  labs(x = "Block number", 
       y = "Z-scored bid offer (relative to each subject's avg and sd)", 
       title = "Bid offers following each block, by subject")

# not faceted by subject
# bid_block_total %>%
#   mutate(subj_id = as.factor(subj_id)) %>%
#   group_by(curr_block_num) %>%
#   ggplot(mapping = aes(x=curr_block_num,y=avg_following_bid_z,fill=subj_id,color=subj_id)) +
#   geom_point(alpha = 0.3,
#              position = position_jitter(height = 0, width = 0.1)) +
#   geom_smooth(method="lm",se=TRUE) +
#   labs(x = "Block number", 
#        y = "Z-scored bid offer (relative to each subject's avg and sd)", 
#        title = "Bid offers following each block, by subject")

# averaged across all participants
bid_block_total %>%
  group_by(curr_block_num) %>%
  ggplot(mapping = aes(x=curr_block_num,y=avg_following_bid_z)) +
  geom_point(alpha = 0.3,
             position = position_jitter(height = 0, width = 0.1)) +
  geom_smooth(method="lm",se=TRUE) +
  labs(x = "Block number", 
       y = "Z-scored bid offer (relative to each subject's avg and sd)", 
       title = "Bid offers following each block, all subjects all blocks")
```

Plotting preceding bid by avg accuracy in following block:
``` {r data_wrangling}
# including all subjects
bid_block_total %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x = avg_preceding_bid_z, y = avg_z_accuracy)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 3) +  # Points colored by block number
  labs(x = "Bid Z-Score",
       y = "Z-scored (by participant) Average Accuracy in Following Block",
       color = "Block Number") +
  ggtitle("Bid Z-Score by Following Average Accuracy for Each Block, across subjects")

# faceted by subjects
bid_block_total %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x = avg_preceding_bid_z, y = avg_z_accuracy)) +
  facet_wrap(~subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 3) +  # Points colored by block number
  labs(x = "Preceding Bid Z-Score",
       y = "Average Accuracy",
       color = "Block Number") +
  ggtitle("Bid Z-Score by Following Average Accuracy for Each Block,by subject")
```

Plotting following bid by avg accuracy in a block:
``` {r data_wrangling}
# including all subjects
bid_block_total %>%
  ggplot(mapping = aes(x = avg_z_accuracy, y = avg_following_bid_z)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 3) +  # Points colored by block number
  labs(x = "Average Z-scored Accuracy",
       y = "Following bid score",
       color = "Block Number") +
  ggtitle("Following Bid Z-Score by Prior Block Accuracy for Each Block, across subjects")

# faceted by subjects
bid_block_total %>%
  ggplot(mapping = aes(x = avg_z_accuracy, y = avg_following_bid_z)) +
  facet_wrap(~subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 3) +  # Points colored by block number
  labs(x = "Avg Z accuracy",
       y = "Following bid score",
       color = "Block Number") +
  ggtitle("Following Bid Z-Score by Prior Block Accuracy for Each Block, by subject")

```
Do the same for reaction time: 
``` {r data_wrangling}
# including all subjects
bid_block_total %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x = avg_preceding_bid_z, y = avg_z_rt)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 3) +  # Points colored by block number
  labs(x = "Bid Z-Score",
       y = "Z-scored (by participant) Average Reaction Time in Following Block",
       color = "Block Number") +
  ggtitle("Bid Z-Score by Following Average Reaction Time for Each Block, across subjects")

# faceted by subjects
bid_block_total %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x = avg_preceding_bid_z, y = avg_z_rt)) +
  facet_wrap(~subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 3) +  # Points colored by block number
  labs(x = "Preceding Bid Z-Score",
       y = "Average Accuracy",
       color = "Block Number") +
  ggtitle("Bid Z-Score by Following Average Reaction Time for Each Block,by subject")
```

``` {r data_wrangling}
# including all subjects
bid_block_total %>%
  ggplot(mapping = aes(x = avg_following_bid_z, y = avg_z_rt)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 3) +  # Points colored by block number
  labs(x = "Following Bid Z-Score",
       y = "Average Z-scored RT",
       color = "Block Number") +
  ggtitle("Average Z-scored Reaction Time by Following Bid Z-Score for Each Block, across subjects")

# faceted by subjects
bid_block_total %>%
  ggplot(mapping = aes(x = avg_following_bid_z, y = avg_z_rt)) +
  facet_wrap(~subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 3) +  # Points colored by block number
  labs(x = "Following Bid Z-Score",
       y = "Average Z-scored RT",
       color = "Block Number") +
  ggtitle("Average Z-scored Reaction Time by Following Bid Z-Score for Each Block, by subject")

```

LOOKING AT AVG COMPARED WITH SWITCH OR NO SWITCH

Looking at overall average accuracy in spatial recall vs in vs, by subject
``` {r data_wrangling}
excluded_switch_data %>%
  mutate(subj_id = as.factor(subj_id)) %>%
  mutate(block_switched = ifelse(block_switched == "false","block did not switch","block switched")) %>%
  group_by(subj_id) %>%
  ggplot(mapping = aes(x=game_type,y=correct)) +
  facet_wrap(~block_switched) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.4,
                                        height = 0.01)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1) +
  labs(x="task type",y="accuracy per trial per subject")+
  ggtitle("Trial accuracy by task type")

excluded_switch_data %>%
  mutate(subj_id = as.factor(subj_id),block_switched = ifelse(block_switched == "false","block did not switch","block switched")) %>%
  ggplot(mapping = aes(x=game_type,y=avg_z_accuracy,color=subj_id)) +
  facet_wrap(~block_switched) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.4,
                                        height = 0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1) +
  labs(x="task type",y="average z-scored accuracy per block per subject")+
  ggtitle("z-scored Block accuracy by task type, across subjects")

excluded_switch_data %>%
  mutate(subj_id = as.factor(subj_id),block_switched = ifelse(block_switched == "false","block did not switch","block switched")) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_z_accuracy,color=subj_id)) +
  facet_wrap(~game_type) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.4,
                                        height = 0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1) +
  labs(x="Is this a switched task",y="z-scored average accuracy per block per subject")+
  ggtitle("Block accuracy by task type, across subjects")
```

Bid offers by switch or not
``` {r data_wrangling}
bid_block_total %>%
  mutate(subj_id = as.factor(subj_id),block_switched = ifelse(block_switched == "false","block did not switch","block switched")) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_following_bid_z,color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  facet_wrap(~game_type)+
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  labs(x="Did the task switch this block?",y="Average bid by participant/block after this block")+
  ggtitle("Relationship between switch status and following bid offer")

```
``` {r data_wrangling}
# to try to visualize this question: if bid offer is in higher bucket, and switch was successful vs unsucessful, how does that change accuracy? (accounting for game type)
breaks <- c(-Inf, -1, 0, 1, Inf)
labels <- c('more than 1 below','0 to 1 below', '0 to 1 above', 'more than 1 above')

bid_block_total_details_binned <- bid_block_total %>%
  mutate(bid_bin_preceding = cut(avg_preceding_bid_z, breaks = breaks, labels = labels, right = FALSE),
         bid_bin_following = cut(avg_following_bid_z, breaks = breaks, labels = labels, right = FALSE))%>%
  mutate(subj_id = as.factor(subj_id),block_switched = ifelse(block_switched == 'false',"no switch","switch")) %>%
  mutate(subj_id = as.factor(subj_id))

bid_block_total_details_binned %>%
  ggplot(mapping = aes(x=block_switched,y=avg_z_accuracy)) +
  facet_wrap(~bid_bin_preceding,ncol=8) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="Average accuracy in this block")+
  ggtitle("Relationship between bid offer, switch status and following average accuracy")
```
``` {r data_wrangling}
# to try to visualize this question: if bid offer is in higher bucket, and switch was successful vs unsucessful, how does that change accuracy? (accounting for game type)
breaks <- c(-Inf, -1, 0, 1, Inf)
labels <- c('more than 1 below','0 to 1 below', '0 to 1 above', 'more than 1 above')

bid_block_total_details_binned %>%
  filter(game_type=="vs") %>%
  ggplot(mapping = aes(x=block_switched,y=avg_z_accuracy)) +
  facet_wrap(~bid_bin_preceding,ncol=8) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="Average accuracy in this block")+
  ggtitle("VS: Relationship between bid offer, switch status and following average accuracy")

bid_block_total_details_binned %>%
  filter(game_type=="spatial_recall") %>%
  ggplot(mapping = aes(x=block_switched,y=avg_z_accuracy)) +
  facet_wrap(~bid_bin_preceding,ncol=8) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="Average accuracy in this block")+
  ggtitle("SR: Relationship between bid offer, switch status and following average accuracy")
```


**BASIC LINEAR MODELS**
``` {r models}
fit.compact = lmer(formula = correct ~ (1 | subj_id),
                   data = final_df)
fit.augmented = lmer(formula = correct ~ preceding_bid_z_score + (1|subj_id),
                     data = final_df)
fit.augmented_two = lmer(formula = correct ~ preceding_bid_z_score + (1 + game_type|subj_id),
                     data = final_df)
fit.augmented_three = lmer(formula = correct ~ preceding_bid_z_score + block_switched + (1 + game_type|subj_id),
                     data = final_df)

anova(fit.compact, fit.augmented)
anova(fit.compact, fit.augmented_two)
anova(fit.compact, fit.augmented_three)

summary(fit.augmented_three)
```
``` {r models}
anova(fit.augmented, fit.augmented_two)
anova(fit.augmented_two, fit.augmented_three)
```

``` {r models}
fit.augmented_four = lmer(formula = correct ~ preceding_bid_z_score*block_switched + (1 + game_type|subj_id),
                     data = final_df)

anova(fit.compact, fit.augmented_four)
anova(fit.augmented_two, fit.augmented_four)
anova(fit.augmented_three, fit.augmented_four)

summary(fit.augmented_four)
```

``` {r models}
fit.augmented_five = lmer(formula = correct ~ preceding_bid_z_score:block_switched + (1 + game_type|subj_id),
                     data = final_df)

anova(fit.compact, fit.augmented_five)
anova(fit.augmented_two, fit.augmented_five)
anova(fit.augmented_three, fit.augmented_five)

summary(fit.augmented_five)
```


``` {r models}
fit.augmented_six = lmer(formula = correct ~ trial_index + preceding_bid_z_score*block_switched + (1 + game_type|subj_id),
                     data = final_df)

anova(fit.compact, fit.augmented_six)
anova(fit.augmented_two, fit.augmented_six)
anova(fit.augmented_three, fit.augmented_six)

summary(fit.augmented_four)
```