---
title: "pilotD_modeling"
output: html_document
date: "2024-08-07"
---
This is the cleaned up version of "pilotD_second_analysis.Rmd" with additional analyses. 

This is from a 100 person "pilotD_second" sample conducted on Prolific from july 26 - august 6.

# TASK INFORMATION:
The spatial recall was 4 squares at a time, and the visual search was conjunction only and 24 items only. 

The setup was:
5 spatial recall practice
15 visual search practice

20 blocks
- 30 visual search per block
- 12 spatial recall per block


# SETUP:
## imports
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("performance")
library(ggplot2)
library(see)
##library(jsonlite)
library("broom")      # for tidying up linear models 
library("car")        # for running ANOVAs
library("afex")       # also for running ANOVAs
library("emmeans")    # for calculating constrasts

# set the default ggplot theme 
theme_set(theme_classic())
```

## Data Loading:
Read in the data: (it's broken up across two folders)
``` {r data_load}

# first folder:
setwd("../../data/pilotD_second/prolific_original")

csv_files <- list.files(pattern = "\\.csv$")

# Function to read a CSV file and convert all columns to character type
read_csv_as_character <- function(file) {
  df <- read.csv(file, stringsAsFactors = FALSE)
  df[] <- lapply(df, as.character)
  return(df)
}

df_all <- bind_rows(lapply(csv_files,read_csv_as_character))
``` 
``` {r data_load}
# second folder:
setwd("../../data/pilotD_second/prolific_copy")
csv_files <- list.files(pattern = "\\.csv$")

# there is some run_id overlap so edit all of the run_ids in this folder
temp <- bind_rows(lapply(csv_files,read_csv_as_character))
temp <- temp %>%
  mutate(run_id = as.character((as.integer(run_id) + 500)))
df_all <- bind_rows(df_all, temp)
```

## data wrangling & pre-processing:

Remove identifiers and uneccesary cols:
``` {r data_wrangling_anon}
anonymize_clean <- function(df) {
  df <- df %>%
    select(-recorded_at,-url,-ip,-user_agent,-referer,-sequence_length,
         -accept_language,-device,-internal_node_id,-view_history,
         -source_code_version, -contains("browser"),-contains("platform"),
         -contains("screen"),-contains("width"),-contains("height"),
         -contains("failed"),-condition,-success,-event_history, -block_num)
  return(df)
}
df_all <- anonymize_clean(df_all)
```

Create a column in df_all for participant ratings of task difficulty/boringness, and of their practice performance. Save all practice trials to a different df called practice_runs_df. Final cleaned df after this is df_all_cleaned
``` {r data_wrangling_add_cols}
# save practice to practice_runs_df
practice_runs_df <- df_all %>%
  filter(practice == "true")

# make a column for how much they rated vs and sr difficulty and boringness
temp <- df_all %>%
  filter(trial_type == "survey-text") %>%
  filter(str_detect(response, "bid_decision") | str_detect(response, "game_description") | str_detect(response, "boring") | str_detect(response, "prolific_id"))

temp <- temp %>%
  mutate(response = map(response, ~ jsonlite::fromJSON(.))) %>%
  unnest_wider(response)

feedback_temp_sr <- temp %>%
  filter(!is.na(sr_boring)) %>%
  select(run_id, sr_boring, sr_difficult)
feedback_temp_vs <- temp %>%
  filter(!is.na(vs_boring)) %>%
  select(run_id, vs_boring, vs_difficult)
prolific_ids_df <- temp %>%
  filter(!is.na(prolific_id)) %>%
  select(run_id, prolific_id)

df_all <- df_all %>%
  left_join(feedback_temp_sr, by = "run_id") %>%
  left_join(feedback_temp_vs, by = "run_id") %>%
  left_join(prolific_ids_df, by = "run_id")

# make a column for average practice score per participant and put it into the main df
temp <- practice_runs_df %>%
  select(run_id, trial_type, score_an, correct_trial) %>%
  mutate(correct = ifelse(trial_type == "spatial-recall",as.integer(score_an),ifelse(correct_trial=="null",0,as.integer(correct_trial)))) %>%
  select(run_id, trial_type, correct) %>%
  group_by(run_id, trial_type) %>%
  summarise(avg_correct = mean(correct)) %>%
  mutate(sr_practice_accuracy = ifelse(trial_type == "spatial-recall",avg_correct,NA),vs_practice_accuracy = ifelse(trial_type != "spatial-recall",avg_correct,NA)) %>%
  ungroup() %>%
  select(run_id, sr_practice_accuracy, vs_practice_accuracy) %>%
  group_by(run_id) %>%
  summarise(
    sr_practice_accuracy = max(sr_practice_accuracy, na.rm = TRUE),
    vs_practice_accuracy = max(vs_practice_accuracy, na.rm = TRUE)
  ) %>%
  ungroup()
df_all <- merge(df_all, temp, by = "run_id")

# remove practice & other non-task rows from df
df_all_cleaned <- df_all %>%
  filter(trial_type != "instructions", trial_type != "preload", 
           trial_type != "survey-multi-choice",
           (trial_type != 'html-keyboard-response' | trial_id =='test_trial'),
           (trial_type != 'html-button-response'),
           !grepl("screen", trial_type, ignore.case = TRUE),
         !str_detect(response, "prolific_id"),
         !str_detect(response, "game_description"),
         !str_detect(response, "boring")) %>%
    filter(practice != "true") %>%
    mutate(bid_value = as.integer(gsub("[^0-9]+", "", response)))%>%
  select(-num_stimuli)

# update correct column for all df_all_cleaned
df_all_cleaned <- df_all_cleaned %>%
  mutate(correct = ifelse(trial_type == "spatial-recall",as.integer(score_an, na.rm = TRUE),ifelse(correct_trial=="null",0,as.integer(correct_trial,na.rm=TRUE)))) %>%
  select(-score_an, -correct_trial) %>%
  ungroup()
```
Distribute the bid value to its corresponding block (so each trial per block says the bid value preceding and following this block). Record which block each group of trials is, remove unnecessary columns, and change the datatypes of necessary columns (i.e. subject id). Save the overall average and sd of each participant for each task (to use for normalizing later, if we choose to).

``` {r data_wrangling_bids_blocks}
# spread bid and blocks completed value onto the entire block
# this new column will be how much the participant bid 
sr_practice_num <- 5
sr_per_block <- 12
vs_practice_num <- 15
vs_per_block <- 30
num_blocks <- 20

# Helper function to add a survey-text row if missing
add_survey_text_row <- function(df) {
  if (nrow(df) > 0 && df$trial_type[1] != "survey-text") {
    new_row <- tibble(
      blocks_completed = '0',
      switch_next_block = 'false',
      trial_type = 'survey-text',
      run_id = as.character(df$run_id[1]),
      trial_index = '-1'
    )
    df <- bind_rows(new_row, df)
  }
  return(df)
}

# Function to process data
process_data <- function(data, per_block) {
  data %>%
    nest(data = everything()) %>%
    mutate(data = map(data, add_survey_text_row)) %>%
    unnest(cols = data) %>%
    mutate(
      switch_next_block = ifelse(switch_next_block == "", NA, switch_next_block),
      group = rep(1:(n() %/% (per_block + 1) + 1), each = (per_block + 1), length.out = n())
    ) %>%
    group_by(group) %>%
    mutate(switch_next_block = as.character(switch_next_block)) %>%
    fill(bid_value, switch_next_block, blocks_completed, .direction = "down") %>%
    ungroup() %>%
    select(-group, -bonus, -overall_accuracy, -score_pc, -score_ls, correct)
}
```

``` {r data_wrangling_bids_tasks}
# Spatial Recall
sr_final <- df_all_cleaned %>%
  filter(
    (prevBlockType == "spatial_recall" & switch_next_block == "false") |
      (prevBlockType == "vs" & switch_next_block == "true") |
      (game_type == "spatial_recall")
  ) %>%
  group_by(run_id)

sr_final <- sr_final %>%
  group_split(run_id) %>%
  map_df(~ process_data(.x, sr_per_block))%>%
  mutate(rt = as.numeric(rt, na.rm = TRUE))

# Visual Search
vs_final <- df_all_cleaned %>%
  filter(
    (prevBlockType == "spatial_recall" & switch_next_block == "true") |
      (prevBlockType == "vs" & switch_next_block == "false") |
      (game_type == "vs")
  ) %>%
  group_by(run_id)

vs_final <- vs_final %>%
  group_split(run_id) %>%
  map_df(~ process_data(.x, vs_per_block)) %>%
  mutate(rt = as.numeric(rt, na.rm = TRUE))
```
``` {r data_wrangling_accuracy}
# For each participant for each task, calc average and sd of performance across blocks and of rt

# for spatial recall: 
temp <- sr_final %>%
  group_by(run_id) %>%
  filter(trial_type == "spatial-recall") %>%
  summarize(avg_sr_correct = mean(correct, na.rm = TRUE), sd_sr_correct = sd(correct,na.rm = TRUE), avg_sr_rt = mean(rt, na.rm=TRUE), sd_sr_rt = sd(rt, na.rm=TRUE)) %>%
  ungroup()
# 
sr_final <- merge(sr_final, temp, by = "run_id") 
#   %>%mutate(z_accuracy_sr = ifelse(sd_sr_correct != 0, ((correct - avg_sr_correct)/sd_sr_correct), 0), z_rt_sr = ifelse(sd_sr_rt != 0, ((rt - avg_sr_rt)/sd_sr_rt),0))

# for visual search:
temp <- vs_final %>%
  group_by(run_id) %>%
  filter(trial_id == "test_trial") %>%
  summarize(avg_vs_correct = mean(correct, na.rm = TRUE), sd_vs_correct = sd(correct,na.rm = TRUE), avg_vs_rt = mean(rt, na.rm=TRUE), sd_vs_rt = sd(rt, na.rm=TRUE)) %>%
  ungroup()
# 
vs_final <- merge(vs_final, temp, by = "run_id") 
#   %>%mutate(z_accuracy_vs = ifelse(sd_vs_correct != 0, ((correct - avg_vs_correct)/sd_vs_correct), 0), z_rt_vs = ifelse(sd_vs_rt != 0, ((rt - avg_vs_rt)/sd_vs_rt),0))


# Combine them all
final_df <- bind_rows(sr_final, vs_final) %>%
  mutate(subj_id = as.numeric(run_id), blocks_completed = as.numeric(blocks_completed,na.RM = TRUE)) %>%
  select(-run_id,-generated_BDM_value,-question_order) %>%
  mutate(curr_block_num = blocks_completed + 1)

final_df <- final_df %>%
  group_by(subj_id, game_type) %>%
  arrange(subj_id,curr_block_num) %>%
  rename(preceding_bid = bid_value)

# calculate average performance overall per subject:
final_df <- final_df %>%
  ungroup()

temp <- final_df %>%
  group_by(subj_id) %>%
  summarize(avg_overall_correct = mean(correct, na.rm = TRUE), sd_overall_correct = sd(correct,na.rm = TRUE), avg_overall_rt = mean(rt, na.rm=TRUE), sd_overall_rt = sd(rt, na.rm=TRUE))%>%
  ungroup()

final_df <- final_df %>%
  left_join(temp, by = "subj_id") %>%
  mutate(z_overall_correct = ifelse(sd_overall_correct != 0, ((correct - avg_overall_correct)/sd_overall_correct), 0), z_overall_rt = ifelse(sd_overall_rt != 0, ((rt - avg_overall_rt)/sd_overall_rt),0))
```
Now everything is in "final_df"

Remove unecessary columns.
``` {r data_wrangling_remove_cols}
final_df <- final_df %>%
  select(-c(target_rectangle_location, missed_response, sequence, backwards, responses, stimulus, time_elapsed, trial_id, trial_duration, stimulus_duration, target_present, correct_response, ITIParams, numberStim, choices, exp_stage, prolific_id, sr_accuracy, vs_accuracy))
```

Z-score participant bids (to normalize them per participant):
``` {r data_wrangling_bids_zscore}
# add following_bid column (participant bid following that block of trials)
temp <- final_df %>%
  filter(trial_type == "survey-text") %>%
  group_by(subj_id) %>%
  arrange(subj_id,blocks_completed) %>%
  mutate(following_bid = lead(preceding_bid)) %>%
  ungroup()

final_df <- final_df %>%
  left_join(temp %>% select(subj_id, curr_block_num, following_bid),
            by = c("subj_id","curr_block_num"))


# get average bids per participant
temp <- final_df %>%
  filter(trial_type == "survey-text", trial_index != "-1") %>%
  group_by(subj_id) %>%
  summarise(avg_bids = mean(preceding_bid,na.rm = TRUE),stdev_bids = sd(preceding_bid, na.rm = TRUE)) %>%
  ungroup()
final_df <- final_df %>%
  left_join(temp, by = "subj_id")

# make a column that represents how different (in sd) the amount they want to switch is from their mean
final_df <- final_df %>%
  mutate(preceding_bid_z_score = if_else(stdev_bids == 0, 0, 
                                         ifelse(is.na(preceding_bid),NA,
                                                ((preceding_bid - avg_bids) / 
                                                   stdev_bids))),
         following_bid_z_score = if_else(stdev_bids == 0, 0, 
                                         ifelse(is.na(following_bid),NA,
                                                ((following_bid - avg_bids) / stdev_bids)))) %>%
  filter(trial_type != "survey-text") %>%
  select(-prevBlockType) %>%
  rename(block_switched=switch_next_block) %>%
  # mutate(z_accuracy = ifelse(game_type == "vs",z_accuracy_vs,z_accuracy_sr), z_rt = ifelse(game_type == "vs",z_rt_vs,z_rt_sr)) %>%
  # mutate(z_rt = as.numeric(z_rt)) %>%
  ungroup()
```

At this point, final_df has all of the relevant data; all of the z-scores are participant specific (for each task and each bid), but it has non-z-scored accuracies as well

In final_df, calculate average performance per block:
``` {r data_wrangling_bids_tasks}
# # calculate average (and z) accuracy and average (and z) rt per block. (this is when it was z'd by subject AND task)
# avg_spatial_recall <- final_df %>%
#   filter(game_type == "spatial_recall") %>%
#   group_by(subj_id, curr_block_num) %>%
#   summarise(avg_z_accuracy = mean(z_accuracy),stdev_z_accuracy = sd(z_accuracy,na.rm = TRUE), avg_z_rt = mean(z_rt_sr, na.rm=TRUE),stdev_z_rt = sd(z_rt_sr,na.rm = TRUE), avg_block_accuracy = mean(correct), sd_block_accuracy = sd(correct),avg_block_rt = mean(rt, na.rm = TRUE), sd_block_rt = sd(rt, na.rm = TRUE), avg_z_overall_block_accuracy = mean(z_overall_correct), sd_overall_block_accuracy = sd(z_overall_correct),avg_z_overall_block_rt = mean(z_overall_rt), sd_overall_block_rt = sd(z_overall_rt))%>%
#   arrange(subj_id,curr_block_num)
# 
# avg_vs <- final_df %>%
#   filter(game_type == "vs") %>%
#   group_by(subj_id, curr_block_num) %>%
#   summarise(avg_z_accuracy = mean(z_accuracy),stdev_z_accuracy = sd(z_accuracy,na.rm = TRUE), avg_z_rt = mean(as.numeric(z_rt_vs),na.rm=TRUE),stdev_z_rt = sd(z_rt_vs,na.rm = TRUE), avg_block_accuracy = mean(correct, na.rm = TRUE), sd_block_accuracy = sd(correct, na.rm = TRUE), avg_block_rt = mean(rt, na.rm = TRUE), sd_block_rt = sd(rt, na.rm = TRUE),avg_z_overall_block_accuracy = mean(z_overall_correct), sd_overall_block_accuracy = sd(z_overall_correct),avg_z_overall_block_rt = mean(z_overall_rt), sd_overall_block_rt = sd(z_overall_rt))%>%
#   arrange(subj_id,curr_block_num)
# 
# avg_per_block <- bind_rows(avg_spatial_recall, avg_vs) %>%
#   arrange(subj_id, curr_block_num)
# 
# final_df <- final_df %>%
#   left_join(avg_per_block, by = c("subj_id","curr_block_num"))


# only z by participant not by both:
# calculate average (and z) accuracy and average (and z) rt per block. (this is when it was z'd by subject AND task)
temp <- final_df %>%
  group_by(subj_id, curr_block_num) %>%
  summarise(avg_z_accuracy = mean(z_overall_correct),stdev_z_accuracy = sd(z_overall_correct,na.rm = TRUE), avg_z_rt = mean(z_overall_rt, na.rm=TRUE),stdev_z_rt = sd(z_overall_rt,na.rm = TRUE), avg_block_accuracy = mean(correct), sd_block_accuracy = sd(correct),avg_block_rt = mean(rt, na.rm = TRUE), sd_block_rt = sd(rt, na.rm = TRUE))%>%
  arrange(subj_id,curr_block_num)
final_df <- final_df %>%
  left_join(temp, by = c("subj_id","curr_block_num"))


# add how many times an individual task has happened
final_df <- final_df %>%
  group_by(subj_id, game_type) %>%
  mutate(task_block_count = cumsum(!duplicated(blocks_completed))) %>%
  ungroup()

# add which trial number every row is within a block
final_df <- final_df %>%
  group_by(subj_id, curr_block_num) %>%
  mutate(trial_count = row_number()) %>%
  ungroup()
```

# PARTICIPANT EXCLUSION

Plot average and median avg subject accuracies for both tasks. Then exclude necessary participants and plot again. 

Exclusion criteria (as of now):
1) participants who never switched between tasks
2) participants who got above 93% accuracy on both tasks (to prevent ceiling effects and to ensure that participants we are studying make some errors); need to adjust this number to be sd above overall mean potentially
3) participants who got below 30% accuracy on both tasks (to prevent inclusion of participants who may not be trying); need to consider this more / adjust this number to be mathematically sound

``` {r performance_pre_exclusion}
temp <- final_df

# temp <- temp %>%
#   select(subj_id, correct, game_type,blocks_completed) %>%
#   arrange(subj_id, game_type, blocks_completed) %>%
#   group_by(subj_id, game_type) %>%
#   mutate(block_count = cumsum(!duplicated(blocks_completed))) %>%
#   ungroup()

# across subjects, how accuracy changes over time per task
temp %>%
  group_by(subj_id) %>%
  ggplot(mapping = aes(x=task_block_count,y=avg_z_accuracy)) +
  facet_wrap(~game_type) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = subj_id), size = 0.5, position = position_jitter(0.1,0)) +  # Points colored by block number
  labs(x = "Blocks Completed of Given Task",
       y = "Z-Accuracy on this block per subject") +
  ggtitle("Z-Average Accuracy Over Time, across subjects pre-exclusion")


# average of all subj averages
temp %>%
  group_by(subj_id, game_type) %>%
  summarise(avg_correct = mean(correct)) %>%
  ggplot(mapping = aes(x=game_type,y=avg_correct)) +
 geom_point(alpha = 0.5,position = position_jitter(width = 0.4,
                              height = 0.01)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game Type",y="Average accuracy on all trials of this game, per subject")+
  ggtitle("Average of subject mean performance on each game (pre-exclusion)")

temp %>%
  group_by(subj_id, game_type) %>%
  summarise(avg_correct = mean(correct)) %>%
  ggplot(mapping = aes(x=game_type,y=avg_correct)) +
 geom_point(alpha = 0.5,position = position_jitter(width = 0.4,
                              height = 0.01)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = median, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game Type",y="Average accuracy on all trials of this game, per subject")+
  ggtitle("Median of subject mean performance on each game (pre-exclusion)")
```

Excluding participants specified above: 
``` {r excluding}

# fill in the final_df missing values per subject
final_df <- final_df %>%
  group_by(subj_id) %>%
  fill(avg_vs_correct, avg_sr_correct, avg_sr_rt, avg_vs_rt, sd_sr_correct, sd_sr_rt, sd_vs_correct, sd_vs_rt, .direction = "downup") %>%
  ungroup()

# cutoffs
top_cutoff = 0.93 # right now, to be cut out must get above this on both tasks
bottom_cutoff = 0.30 # right now, to be cut out must get below this on both tasks

# get subjects who never switched
subjects_no_switch <- final_df %>%
  group_by(subj_id) %>%
  summarize(has_spatial_recall = any(game_type == "spatial_recall"), has_vs = any(game_type == "vs")) %>%
  filter(!has_spatial_recall | !has_vs)
head(subjects_no_switch)

# get subjects above the cutoff on both tasks
subjects_high_low_accuracy <- final_df %>%
  select(subj_id, avg_vs_correct, avg_sr_correct) %>%
  group_by(subj_id) %>%
  summarize(min_avg_score = min(avg_vs_correct, avg_sr_correct), max_avg_score = max(avg_vs_correct, avg_sr_correct)) %>%
  filter(min_avg_score > top_cutoff | max_avg_score < bottom_cutoff)
head(subjects_high_low_accuracy)

# combine list of exclusions
subjects_high_low_accuracy <- subjects_high_low_accuracy %>%
  select(subj_id)
subjects_no_switch <- subjects_no_switch %>%
  select(subj_id)
excluded_participants <- bind_rows(subjects_high_low_accuracy, subjects_no_switch)

final_df_excluded <- final_df %>%
  anti_join(excluded_participants, by = "subj_id") %>%
  ungroup()
```
``` {r performance_post_exclusion}
temp <- final_df_excluded


# across subjects, how accuracy changes over time per task
temp %>%
  group_by(subj_id) %>%
  ggplot(mapping = aes(x=task_block_count,y=avg_z_accuracy)) +
  facet_wrap(~game_type) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = subj_id), size = 0.5, position = position_jitter(0.1,0)) +  # Points colored by block number
  labs(x = "Blocks Completed of Given Task",
       y = "Z-Accuracy on this block per subject") +
  ggtitle("Z-Average Accuracy Over Time, across subjects post-exclusion")


# average of all subj averages
temp %>%
  group_by(subj_id, game_type) %>%
  summarise(avg_correct = mean(correct)) %>%
  ggplot(mapping = aes(x=game_type,y=avg_correct)) +
 geom_point(alpha = 0.5,position = position_jitter(width = 0.4,
                              height = 0.01)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game Type",y="Average accuracy on all trials of this game, per subject")+
  ggtitle("Average of subject mean performance on each game (post-exclusion)")

temp %>%
  group_by(subj_id, game_type) %>%
  summarise(avg_correct = mean(correct)) %>%
  ggplot(mapping = aes(x=game_type,y=avg_correct)) +
 geom_point(alpha = 0.5,position = position_jitter(width = 0.4,
                              height = 0.01)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = median, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game Type",y="Average accuracy on all trials of this game, per subject")+
  ggtitle("Median of subject mean performance on each game (post-exclusion)")
```

# PLOTTING
## How boring / difficult participants found each task
``` {r plot_boring_diff}
# add difficulty and boringness difference
final_df_excluded <- final_df_excluded %>%
  mutate(vs_boring = as.numeric(vs_boring, na.rm = TRUE), vs_difficult = as.numeric(vs_difficult, na.rm = TRUE), sr_boring = as.numeric(sr_boring, na.rm = TRUE), sr_difficult = as.numeric(sr_difficult, na.rm = TRUE)) %>%
  mutate(more_boring = ifelse(vs_boring > sr_boring, "visual-search","spatial-recall"), more_difficult = ifelse(vs_difficult > sr_difficult, "visual-search","spatial-recall"), boring_difference = abs(vs_boring - sr_boring), difficulty_difference = abs(vs_difficult - sr_difficult))

# get one row per subject
temp <- final_df_excluded %>%
  group_by(subj_id) %>%
  filter(curr_block_num == 1, trial_count == 1)

# boring difference
temp %>% 
  select(subj_id, boring_difference, more_boring) %>%
  ggplot(mapping = aes(x=boring_difference, color = more_boring)) +
  geom_histogram() +
  labs(x = "difference in rated boringness", y = "number of subjects", title = "Difference in boring rating (1-100) between sr and vs")

# difficulty difference
temp %>% 
  select(subj_id, difficulty_difference, more_difficult) %>%
  ggplot(mapping = aes(x=difficulty_difference, color = more_difficult)) +
  geom_histogram() +
  labs(x = "difference in rated difficulty", y = "number of subjects", title = "Difference in difficulty rating (1-100) between sr and vs")
```

## (normalized per participant) Bids over time:

``` {r plot_bid_time}
# faceted by subject
final_df_excluded %>%
  group_by(subj_id, curr_block_num) %>%
  summarise(following_z_bid = mean(following_bid_z_score)) %>%
  ggplot(mapping = aes(x=curr_block_num,y=following_z_bid,fill=subj_id,color=subj_id)) +
  geom_point(alpha = 0.15,
             position = position_jitter(height = 0, width = 0.2), size = 1) +
  facet_wrap(~subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  labs(x = "Block number", 
       y = "Z-scored bid offer (relative to each subject's avg and sd)", 
       title = "Bid offers following each block, by subject")

# averaged across all participants
final_df_excluded %>%
  filter(trial_count == 1) %>%
  ggplot(mapping = aes(x=curr_block_num,y=following_bid_z_score, color = subj_id)) +
  geom_point(alpha = 0.15,
             position = position_jitter(height = 0, width = 0.2), size = 1) +
  geom_smooth(method="lm",se=TRUE) +
  labs(x = "Block number", 
       y = "Z-scored bid offer (relative to each subject's avg and sd)", 
       title = "Bid offers following each block, all subjects all blocks")

library(viridis)
final_df_excluded %>%
  group_by(subj_id) %>%
  filter(trial_count == 1) %>%
  ggplot(mapping = aes(x=curr_block_num,y=following_bid_z_score, group=subj_id, color=subj_id)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(alpha = 0.15,
             position = position_jitter(height = 0, width = 0.2), size = 1) +
  scale_color_viridis(discrete = FALSE) + # Apply a viridis color theme
  theme_minimal() +
  labs(x = "Block number", 
       y = "Z-scored bid offer (relative to each subject's avg and sd)", 
       title = "Bid offers following each block, all subjects all blocks")
```

## (non-normalized) Block Accuracy and RT by (normalized) Following Bids 

Not normalizing per participant means we are looking at **how well participants perform relative to how well they normally perform on this task and relative to how well they perform on the other task**

``` {r data_wrangling}
# including all subjects
final_df_excluded %>%
  ungroup() %>%
  # group_by(subj_id, following_bid_z_score, avg_block_accuracy) %>%
  ggplot(mapping = aes(x = following_bid_z_score, y = avg_block_accuracy)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 2) +  # Points colored by block number
  labs(x = "Bid Z-Score",
       y = "Average Accuracy in Previous Block",
       color = "Block Number") +
  ggtitle("Prior Block's Average Accuracy by Z-Scored Bid, all subjects")

# faceted by subjects, show first few
final_df_excluded %>%
  filter(subj_id < 20) %>%
  ggplot(mapping = aes(x = following_bid_z_score, y = avg_block_accuracy)) +
  facet_wrap(~subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 0.05) +  # Points colored by block number
  labs(x = "Bid Z-Score",
       y = "Average Accuracy in Previous Block",
       color = "Block Number") +
  ggtitle("Prior Block's Average Accuracy by Z-Scored Bid, by subject")
```
``` {r data_wrangling}
# including all subjects
final_df_excluded %>%
  ungroup() %>%
  filter(trial_count ==1) %>%
  mutate(game_type = as.factor(game_type),
         curr_block_num = as.factor(curr_block_num)) %>%
  ggplot(mapping = aes(x = following_bid_z_score, y = avg_block_rt, group = game_type)) +
  geom_smooth(mapping = aes(color = game_type), method="lm", se=TRUE) +
  geom_point(size = 1, alpha = 0.2) +  # Points colored by block number
  labs(x = "Bid Z-Score",
       y = "Average RT in Previous Block",
       color = "Block Number") +
  ggtitle("Prior Block's Average RT by Z-Scored Bid, all subjects")

# faceted by subjects, show first few
final_df_excluded %>%
  filter(subj_id < 20) %>%
  ggplot(mapping = aes(x = following_bid_z_score, y = avg_block_rt, group = game_type, color=game_type)) +
  facet_wrap(~subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(size = 0.05) +  # Points colored by block number
  labs(x = "Bid Z-Score",
       y = "Average RT in Previous Block",
       color = "Block Number") +
  ggtitle("Prior Block's Average RT by Z-Scored Bid, by subject")
```


## (normalized per participant) Block Accuracy and RT by (normalized per participant) Following Bids 

Normalizing per participant means we are looking at **how well participants perform relative to how well they normally perform on this task**

``` {r data_wrangling}
# including all subjects
final_df_excluded %>%
  filter(trial_count == 1) %>%
  group_by(subj_id, following_bid_z_score, avg_z_accuracy) %>%
  ggplot(mapping = aes(x = following_bid_z_score, y = avg_z_accuracy)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 2) +  # Points colored by block number
  labs(x = "Bid Z-Score",
       y = "Average Accuracy in Previous Block, z-scored by subject",
       color = "Block Number") +
  ggtitle("Prior Block's Average z-scored Accuracy by Z-Scored Bid, all subjects")

# faceted by subjects, show first few
final_df_excluded %>%
  filter(subj_id < 20) %>%
  ggplot(mapping = aes(x = following_bid_z_score, y = avg_z_accuracy)) +
  facet_wrap(~subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 0.05) +  # Points colored by block number
  labs(x = "Bid Z-Score",
       y = "Average Accuracy in Previous Block, z-scored by subject",
       color = "Block Number") +
  ggtitle("Prior Block's Average z-scored Accuracy by Z-Scored Bid, all subjects")


# switch axes
final_df_excluded %>%
  filter(trial_count == 1) %>%
  group_by(subj_id, following_bid_z_score, avg_z_accuracy) %>%
  ggplot(mapping = aes(x = avg_z_accuracy, y = following_bid_z_score)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 2) +  # Points colored by block number
  labs(x = "Average Accuracy in Previous Block, z-scored by subject",
       y = "Bid Z-Score",
       color = "Block Number") +
  ggtitle("Prior Block's Average z-scored Accuracy by Z-Scored Bid, all subjects")
```

To do reaction time, must do it per task:
``` {r data_wrangling}
# # including all subjects
# final_df_excluded %>%
#   group_by(subj_id, following_bid_z_score, avg_z_rt) %>%
#   ggplot(mapping = aes(x = following_bid_z_score, y = avg_z_rt)) +
#   geom_smooth(method="lm",se=TRUE) +
#   geom_point(mapping = aes(color = curr_block_num), size = 2) +  # Points colored by block number
#   labs(x = "Bid Z-Score",
#        y = "Average RT in Previous Block, z-scored by subject/task",
#        color = "Block Number") +
#   ggtitle("Prior Block's Average z-scored RT by Z-Scored Bid, all subjects")
# 
# # faceted by subjects, show first few
# final_df_excluded %>%
#   filter(subj_id < 20) %>%
#   ggplot(mapping = aes(x = following_bid_z_score, y = avg_z_rt)) +
#   facet_wrap(~subj_id) +
#   geom_smooth(method="lm",se=TRUE) +
#   geom_point(mapping = aes(color = curr_block_num), size = 0.05) +  # Points colored by block number
#   labs(x = "Bid Z-Score",
#        y = "Average RT in Previous Block, z-scored by subject/task",
#        color = "Block Number") +
#   ggtitle("Prior Block's Average z-scored RT by Z-Scored Bid, all subjects")

final_df_excluded %>%
  filter(game_type == "vs", trial_count==1) %>%
  group_by(subj_id, following_bid_z_score, avg_z_rt) %>%
  ggplot(mapping = aes(x = following_bid_z_score, y = avg_z_rt)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 2) +  # Points colored by block number
  labs(x = "Bid Z-Score",
       y = "Average RT in Previous Block, z-scored by subject",
       color = "Block Number") +
  ggtitle("VS: Prior Block's Average z-scored RT by Z-Scored Bid, all subjects")

final_df_excluded %>%
  filter(game_type == "spatial_recall", trial_count == 1) %>%
  group_by(subj_id, following_bid_z_score, avg_z_rt) %>%
  ggplot(mapping = aes(x = following_bid_z_score, y = avg_z_rt)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 2) +  # Points colored by block number
  labs(x = "Bid Z-Score",
       y = "Average RT in Previous Block, z-scored by subject",
       color = "Block Number") +
  ggtitle("SR: Prior Block's Average z-scored RT by Z-Scored Bid, all subjects")



# flip axes

final_df_excluded %>%
  filter(game_type == "vs", trial_count==1) %>%
  group_by(subj_id, following_bid_z_score, avg_z_rt) %>%
  ggplot(mapping = aes(x = avg_z_rt, y = following_bid_z_score)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 2) +  # Points colored by block number
  labs(x = "Average RT in Previous Block, z-scored by subject",
       y = "Bid Z-Score",
       color = "Block Number") +
  ggtitle("VS: Prior Block's Average z-scored RT by Z-Scored Bid, all subjects")

final_df_excluded %>%
  filter(game_type == "spatial_recall", trial_count == 1) %>%
  group_by(subj_id, following_bid_z_score, avg_z_rt) %>%
  ggplot(mapping = aes(x = avg_z_rt, y = following_bid_z_score)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 2) +  # Points colored by block number
  labs(x = "Average RT in Previous Block, z-scored by subject",
       y = "Bid Z-Score",
       color = "Block Number") +
  ggtitle("SR: Prior Block's Average z-scored RT by Z-Scored Bid, all subjects")
```


## Relationship between (normalized per participant) bid offer, switch status and following (non-normalized) average accuracy and RT

Not normalizing per participant means we are looking at **how well participants perform relative to how well they normally perfom on this task and relative to how well they perform on the other task**

``` {r plot_accuracy_switch_bid}
# to try to visualize this question: if bid offer is in higher bucket, and switch was successful vs unsucessful, how does that change accuracy? (accounting for game type)
breaks <- c(-Inf, -1, 0, 1, Inf)
labels <- c('more than 1 sd <','0 to 1 sd <', '0 to 1 sd >', 'more than 1 sd >')

temp <- final_df_excluded %>%
  group_by(subj_id, curr_block_num, avg_block_accuracy, following_bid_z_score, preceding_bid_z_score, block_switched) %>%
  summarise(preceding_bid_z_score = mean(preceding_bid_z_score), following_bid_z_score =mean(following_bid_z_score), avg_block_accuracy = mean(avg_block_accuracy)) %>%
  mutate(bid_bin_preceding = cut(preceding_bid_z_score, breaks = breaks, labels = labels, right = FALSE),
         bid_bin_following = cut(following_bid_z_score, breaks = breaks, labels = labels, right = FALSE))%>%
  mutate(block_switched = ifelse(block_switched == 'false',"no switch","switch"))

temp %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_block_accuracy)) +
  facet_wrap(~bid_bin_preceding,ncol=8) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="Average accuracy in this block")+
  ggtitle("bid offer (z-scored), switch status and following average accuracy")
```
``` {r plot_RT_switch_bid}
# to try to visualize this question: if bid offer is in higher bucket, and switch was successful vs unsucessful, how does that change accuracy? (accounting for game type)
breaks <- c(-Inf, -1, 0, 1, Inf)
labels <- c('more than 1 sd <','0 to 1 sd <', '0 to 1 sd >', 'more than 1 sd >')

temp <- final_df_excluded %>%
  group_by(subj_id, curr_block_num, avg_block_rt, following_bid_z_score, preceding_bid_z_score, block_switched) %>%
  summarise(preceding_bid_z_score = mean(preceding_bid_z_score), following_bid_z_score =mean(following_bid_z_score), avg_block_rt = mean(avg_block_rt, NA.rm=TRUE)) %>%
  mutate(bid_bin_preceding = cut(preceding_bid_z_score, breaks = breaks, labels = labels, right = FALSE),
         bid_bin_following = cut(following_bid_z_score, breaks = breaks, labels = labels, right = FALSE))%>%
  mutate(block_switched = ifelse(block_switched == 'false',"no switch","switch"))

temp_vs <- final_df_excluded %>%
  filter(game_type == "vs") %>%
  group_by(subj_id, curr_block_num, avg_block_rt, following_bid_z_score, preceding_bid_z_score, block_switched) %>%
  summarise(preceding_bid_z_score = mean(preceding_bid_z_score), following_bid_z_score =mean(following_bid_z_score), avg_block_rt = mean(avg_block_rt, NA.rm=TRUE)) %>%
  mutate(bid_bin_preceding = cut(preceding_bid_z_score, breaks = breaks, labels = labels, right = FALSE),
         bid_bin_following = cut(following_bid_z_score, breaks = breaks, labels = labels, right = FALSE))%>%
  mutate(block_switched = ifelse(block_switched == 'false',"no switch","switch"))

temp_sr <- final_df_excluded %>%
    filter(game_type == "spatial_recall") %>%
  group_by(subj_id, curr_block_num, avg_block_rt, following_bid_z_score, preceding_bid_z_score, block_switched) %>%
  summarise(preceding_bid_z_score = mean(preceding_bid_z_score), following_bid_z_score =mean(following_bid_z_score), avg_block_rt = mean(avg_block_rt, NA.rm=TRUE)) %>%
  mutate(bid_bin_preceding = cut(preceding_bid_z_score, breaks = breaks, labels = labels, right = FALSE),
         bid_bin_following = cut(following_bid_z_score, breaks = breaks, labels = labels, right = FALSE))%>%
  mutate(block_switched = ifelse(block_switched == 'false',"no switch","switch"))

temp %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_block_rt)) +
  facet_wrap(~bid_bin_preceding,ncol=8) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="Average RT in this block")+
  ggtitle("bid offer (z-scored), switch status and following average RT")


temp_vs %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_block_rt)) +
  facet_wrap(~bid_bin_preceding,ncol=8) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="Average RT in this block")+
  ggtitle("VS: bid offer (z-scored), switch status and following average RT")

temp_sr %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_block_rt)) +
  facet_wrap(~bid_bin_preceding,ncol=8) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="Average RT in this block")+
  ggtitle("SR: bid offer (z-scored), switch status and following average RT")
```


## Relationship between (normalized per participant) bid offer, switch status and following (normalized per participant) average accuracy and RT

Normalizing per participant means we are looking at **how well participants perform relative to how well they normally perform on this experiment**

``` {r plot_accuracy_switch_bid}
# to try to visualize this question: if bid offer is in higher bucket, and switch was successful vs unsucessful, how does that change accuracy? (accounting for game type)
breaks <- c(-Inf, -1, 0, 1, Inf)
labels <- c('more than 1 sd <','0 to 1 sd <', '0 to 1 sd >', 'more than 1 sd >')

temp <- final_df_excluded %>%
  group_by(subj_id, curr_block_num, avg_z_accuracy, following_bid_z_score, preceding_bid_z_score, block_switched) %>%
  summarise(preceding_bid_z_score = mean(preceding_bid_z_score), following_bid_z_score =mean(following_bid_z_score), avg_z_accuracy = mean(avg_z_accuracy)) %>%
  mutate(bid_bin_preceding = cut(preceding_bid_z_score, breaks = breaks, labels = labels, right = FALSE),
         bid_bin_following = cut(following_bid_z_score, breaks = breaks, labels = labels, right = FALSE))%>%
  mutate(block_switched = ifelse(block_switched == 'false',"no switch","switch"))

temp %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_z_accuracy)) +
  facet_wrap(~bid_bin_preceding,ncol=8) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="Average (z-scored) accuracy in this block")+
  ggtitle("bid offer (z-scored), switch status and following average accuracy (z-scored by participant)")

# broken up into game
temp <- final_df_excluded %>%
  filter(game_type == "vs") %>%
  group_by(subj_id, curr_block_num, avg_z_accuracy, following_bid_z_score, preceding_bid_z_score, block_switched) %>%
  summarise(preceding_bid_z_score = mean(preceding_bid_z_score), following_bid_z_score =mean(following_bid_z_score), avg_z_accuracy = mean(avg_z_accuracy)) %>%
  mutate(bid_bin_preceding = cut(preceding_bid_z_score, breaks = breaks, labels = labels, right = FALSE),
         bid_bin_following = cut(following_bid_z_score, breaks = breaks, labels = labels, right = FALSE))%>%
  mutate(block_switched = ifelse(block_switched == 'false',"no switch","switch"))

temp %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_z_accuracy)) +
  facet_wrap(~bid_bin_preceding,ncol=8) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="Average (z-scored) accuracy in this block")+
  ggtitle("VS: bid offer (z-scored), switch status and following average accuracy (z-scored by participant)")

temp <- final_df_excluded %>%
  filter(game_type == "spatial_recall") %>%
  group_by(subj_id, curr_block_num, avg_z_accuracy, following_bid_z_score, preceding_bid_z_score, block_switched) %>%
  summarise(preceding_bid_z_score = mean(preceding_bid_z_score), following_bid_z_score =mean(following_bid_z_score), avg_z_accuracy = mean(avg_z_accuracy)) %>%
  mutate(bid_bin_preceding = cut(preceding_bid_z_score, breaks = breaks, labels = labels, right = FALSE),
         bid_bin_following = cut(following_bid_z_score, breaks = breaks, labels = labels, right = FALSE))%>%
  mutate(block_switched = ifelse(block_switched == 'false',"no switch","switch"))

temp %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_z_accuracy)) +
  facet_wrap(~bid_bin_preceding,ncol=8) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="Average (z-scored) accuracy in this block")+
  ggtitle("SR: bid offer (z-scored), switch status and following average accuracy (z-scored by participant)")



# REMOVING FIRST TRIAL
temp <- final_df_excluded %>%
  filter(trial_count != 1) %>%
  group_by(subj_id, curr_block_num) %>%
  summarise(preceding_bid_z_score = mean(preceding_bid_z_score), following_bid_z_score =mean(following_bid_z_score), avg_z_block_accuracy = mean(z_overall_correct), block_switched = block_switched, trial_count = trial_count) %>%
  mutate(bid_bin_preceding = cut(preceding_bid_z_score, breaks = breaks, labels = labels, right = FALSE),
         bid_bin_following = cut(following_bid_z_score, breaks = breaks, labels = labels, right = FALSE))%>%
  mutate(block_switched = ifelse(block_switched == 'false',"no switch","switch")) %>%
  filter(trial_count == 2)#keep only one row per block per subj bc avgs are the same


temp %>%
  filter(curr_block_num !=1) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_z_block_accuracy)) +
  facet_wrap(~bid_bin_preceding,ncol=8) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="Average (z-scored) accuracy in this block")+
  ggtitle("NO TRIAL 1 bid offer (z-scored), switch status and following average accuracy (z-scored by participant)")


# REMOVING FIRST TWO TRIALS
temp <- final_df_excluded %>%
  filter(trial_count != 1 & trial_count != 2) %>%
  group_by(subj_id, curr_block_num) %>%
  summarise(preceding_bid_z_score = mean(preceding_bid_z_score), following_bid_z_score =mean(following_bid_z_score), avg_z_block_accuracy = mean(z_overall_correct), block_switched = block_switched, trial_count = trial_count) %>%
  mutate(bid_bin_preceding = cut(preceding_bid_z_score, breaks = breaks, labels = labels, right = FALSE),
         bid_bin_following = cut(following_bid_z_score, breaks = breaks, labels = labels, right = FALSE))%>%
  mutate(block_switched = ifelse(block_switched == 'false',"no switch","switch")) %>%
  filter(trial_count == 3)#keep only one row per block per subj bc avgs are the same


temp %>%
  filter(curr_block_num !=1) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_z_block_accuracy)) +
  facet_wrap(~bid_bin_preceding,ncol=8) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="Average (z-scored) accuracy in this block")+
  ggtitle("NO TRIAL 1-2 bid offer (z-scored), switch status and following average accuracy (z-scored by participant)")
```

# MORE LOOKING INTO THE DATA

## LOOK AT SWITCH COST BY LOOKING AT FIRST 5 TRIALS OF EVERY BLOCK BY switch vs not switch

``` {r plot_switch_cost}
# look at blocks 7 and 8 as an example
filtered <- final_df_excluded %>%
  ungroup() %>%
  filter(curr_block_num %in% c(4,5,6,7,8,9,10,11,12))

# get first 5 trials of each given block to plot
filtered <- filtered %>%
  group_by(subj_id, curr_block_num, block_switched) %>%
  mutate(block_switched = ifelse(block_switched == "true","switched","didn't switch"))%>%
  slice_head(n = 5) %>%
  ungroup() 

ggplot(filtered, aes(x = block_switched, y = z_overall_correct)) +
  facet_wrap(~ curr_block_num) +
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x = "Did they switch?", y = "Trial Accuracy (z-scored by participant)", title = "Switch Cost: Accuracy for the First 5 Trials by Block")

ggplot(filtered, aes(x = block_switched, y = correct)) +
  facet_wrap(~ curr_block_num) +
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x = "Did they switch?", y = "Raw Trial Accuracy", title = "Switch Cost: Accuracy for the First 5 Trials by Block")

# look at vs and sr separately with raw data
ggplot(filtered%>% filter(game_type == "vs"), aes(x = block_switched, y = correct)) +
  facet_wrap(~ curr_block_num) +
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x = "Did they switch?", y = "Raw Trial Accuracy", title = "VS Switch Cost: Accuracy for the First 5 Trials by Block")

ggplot(filtered%>% filter(game_type == "spatial_recall"), aes(x = block_switched, y = correct)) +
  facet_wrap(~ curr_block_num) +
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x = "Did they switch?", y = "Raw Trial Accuracy", title = "SR Switch Cost: Accuracy for the First 5 Trials by Block")


## LOOK AT INdIViDUAL SUBJECT TRENDS (see if first few trials in a block have a lower performance compared to rest)
filtered <- final_df_excluded %>%
  ungroup() %>%
  filter(subj_id <20, block_switched == "true")

# get first 10 trials of each given block to plot
filtered <- filtered %>%
  group_by(subj_id, curr_block_num) %>%
  mutate(block_switched = ifelse(block_switched == "true","switched","didn't switch"))%>%
  slice_head(n = 5) %>%
  mutate(trial_count = row_number()) %>%
  ungroup() %>%
  arrange(subj_id,curr_block_num, trial_count)

ggplot(filtered%>% filter(game_type == "vs"), aes(x = trial_count, y = correct, color = curr_block_num)) +
  facet_wrap(~ subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  labs(x = "Time", y = "Raw Trial Accuracy", title = "VS Switch Cost: Accuracy for the First 5 Trials by Block")

ggplot(filtered%>% filter(game_type == "spatial_recall"), aes(x = trial_count, y = correct, color=curr_block_num)) +
  facet_wrap(~ subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  labs(x = "Time", y = "Raw Trial Accuracy", title = "SR Switch Cost: Accuracy for the First 5 Trials by Block")
```

Plot the same plots with only the first trial from each block, and also plot avg lines of first x trials of blocks that switched and blocks that didnt switch (to see if the trend is the same for both types)

``` {r plot_switch_cost_extra}
breaks <- c(-Inf, -1, 0, 1, Inf)
labels <- c('more than 1 sd <','0 to 1 sd <', '0 to 1 sd >', 'more than 1 sd >')

temp <- final_df_excluded %>%
  filter(trial_count == 1)%>%
  group_by(subj_id, curr_block_num, z_overall_correct, following_bid_z_score, preceding_bid_z_score, block_switched) %>%
  summarise(preceding_bid_z_score = mean(preceding_bid_z_score), following_bid_z_score =mean(following_bid_z_score), z_overall_correct = z_overall_correct, z_overall_rt = z_overall_rt, game_type = game_type) %>%
  mutate(bid_bin_preceding = cut(preceding_bid_z_score, breaks = breaks, labels = labels, right = FALSE),
         bid_bin_following = cut(following_bid_z_score, breaks = breaks, labels = labels, right = FALSE))%>%
  mutate(block_switched = ifelse(block_switched == 'false',"no switch","switch"))

temp %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x=block_switched,y=z_overall_correct, color = subj_id)) +
  facet_wrap(~bid_bin_preceding,ncol=8) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="z-accuracy on first trial of this block")+
  ggtitle("First trial per block: bid offer (z-scored), switch status and following z-accuracy on trial 1")



temp %>%
  filter(curr_block_num != 1, game_type == "spatial_recall") %>%
  ggplot(mapping = aes(x=block_switched,y=z_overall_correct, color = subj_id)) +
  facet_wrap(~bid_bin_preceding,ncol=8) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="z-accuracy on first trial of this block")+
  ggtitle("SR: First trial per block: bid offer (z-scored), switch status and following z-accuracy on trial 1")


temp %>%
  filter(curr_block_num != 1, game_type == "vs") %>%
  ggplot(mapping = aes(x=block_switched,y=z_overall_correct, color = subj_id)) +
  facet_wrap(~bid_bin_preceding,ncol=8) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="z-accuracy on first trial of this block")+
  ggtitle("VS: First trial per block: bid offer (z-scored), switch status and following z-accuracy on trial 1")




temp %>%
  filter(curr_block_num != 1, game_type == "spatial_recall") %>%
  ggplot(mapping = aes(x=block_switched,y=z_overall_rt, color = subj_id)) +
  facet_wrap(~bid_bin_preceding,ncol=8) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="z-rt on first trial of this block")+
  ggtitle("SR: First trial per block: bid offer (z-scored), switch status and following z-rt")


temp %>%
  filter(curr_block_num != 1, game_type == "vs") %>%
  ggplot(mapping = aes(x=block_switched,y=z_overall_rt, color = subj_id)) +
  facet_wrap(~bid_bin_preceding,ncol=8) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.2,position = position_jitter(width=0.3,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="z-rt on first trial of this block")+
  ggtitle("VS: First trial per block: bid offer (z-scored), switch status and following z-rt")

```
``` {r plot_switch_cost_extra}
breaks <- c(-Inf, -1, 0, 1, Inf)
labels <- c('more than 1 sd <','0 to 1 sd <', '0 to 1 sd >', 'more than 1 sd >')

temp <- final_df_excluded %>%
  filter(trial_count <= 4)%>%
  mutate(block_switched = ifelse(block_switched == 'false',"no switch","switch"), trial_group = ifelse(trial_count <= 2, "trials 1-2","trials 3-4"))

temp %>% 
  ggplot(mapping = aes(x=trial_count, z_overall_correct, group = interaction(trial_group,block_switched), color=trial_group)) +
  geom_point(alpha = 0.3, size=0.5, position=position_jitter(0.1,0)) +
  geom_smooth(method="lm",se=TRUE) +
  labs(x = "Trial number within block",y = "Z-scored accuracy in each trial, by subject") +
  facet_wrap(~ block_switched)



temp %>% 
  filter(game_type == "vs") %>%
  ggplot(mapping = aes(x=trial_count, z_overall_correct, group = interaction(trial_group,block_switched), color=trial_group)) +
  geom_point(alpha = 0.3, size=0.5, position=position_jitter(0.1,0)) +
  geom_smooth(method="lm",se=TRUE) +
  labs(x = "Trial number within block",y = "Z-scored accuracy in each trial, by subject", title="VS switch cost") +
  facet_wrap(~ block_switched)


temp %>% 
  filter(game_type == "spatial_recall") %>%
  ggplot(mapping = aes(x=trial_count, z_overall_correct, group = interaction(trial_group,block_switched), color=trial_group)) +
  geom_point(alpha = 0.3, size=0.5, position=position_jitter(0.1,0)) +
  geom_smooth(method="lm",se=TRUE) +
  labs(x = "Trial number within block",y = "Z-scored accuracy in each trial, by subject", title="Spatial Recall switch cost") +
  facet_wrap(~ block_switched)

```



## LOOK AT DIFF IN BIDDING FOR PARTICIPANTS WHEN THEY"RE IN GAME A VS GAME B
Can color by what they rated as more boring or more difficult

``` {r plot_diff_bids}
temp <- final_df_excluded %>%
  filter(trial_count == 1) # to get one val per block

# get how much each subject bids on avg when potentially switching to spatial recall
# filter by bids after blocks of visual search
temp_switch_from_vs <- temp %>%
  filter(game_type == "vs") %>%
  group_by(subj_id) %>%
  summarise(avg_bid_from_vs = mean(following_bid))


# get how much each subject bids on avg when potentially switching to vs
# filter by bids after blocks of sr
temp_switch_from_sr <- temp %>%
  filter(game_type == "spatial_recall") %>%
  group_by(subj_id) %>%
  summarise(avg_bid_from_sr = mean(following_bid))

# combine the dfs
temp <- temp %>%left_join(temp_switch_from_sr, by="subj_id")
temp <- temp %>% left_join(temp_switch_from_vs, by="subj_id")%>%
  arrange(subj_id, curr_block_num)

# calc the diff between bids and also which one was bid for higher
temp <- temp %>%
  mutate(bids_task_diff = abs(avg_bid_from_sr - avg_bid_from_vs),
         higher_bid_from = case_when(
           avg_bid_from_sr > avg_bid_from_vs ~ "higher avg bid to switch from sr",
           avg_bid_from_sr < avg_bid_from_vs ~ "higher avg bid to switch from vs",
           TRUE ~ "avg bids are equal"
         ),
         higher_bid_from_simp = case_when(
           avg_bid_from_sr > avg_bid_from_vs ~ "spatial-recall",
           avg_bid_from_sr < avg_bid_from_vs ~ "visual-search",
           TRUE ~ "equal"
         ))

# plot this difference
temp %>%
  filter(curr_block_num == 1) %>%
  ggplot(mapping = aes(x=bids_task_diff, group=higher_bid_from, color=higher_bid_from)) +
  geom_histogram() +
  labs(x="difference between subjects' avg bids to switch from vs or sr", y = "number of subjects",title="Task differences in bidding")


# see how higher bid to switch from corresponds to what task they thought was more boring and what task they thought was more difficult
temp %>%
  filter(curr_block_num == 1, !is.na(more_boring), !is.na(more_difficult), higher_bid_from_simp != "equal") %>%
  select(subj_id, higher_bid_from_simp, more_boring, more_difficult) %>%
  mutate(boring_higher_bid_aligns = ifelse(higher_bid_from_simp == more_boring, TRUE, FALSE),
         difficulty_higher_bid_aligns = ifelse(higher_bid_from_simp == more_difficult, TRUE, FALSE),
         boring_difficulty_aligns = ifelse(more_difficult == more_boring, TRUE, FALSE)) %>%
  mutate(what_aligns = case_when(
           boring_higher_bid_aligns & difficulty_higher_bid_aligns ~ "boring, bidded more to switch from, difficult",
           boring_higher_bid_aligns & !difficulty_higher_bid_aligns ~ "boring, bidded more to switch from",
           !boring_higher_bid_aligns & difficulty_higher_bid_aligns ~ "difficult, bidded more to switch from",
           !boring_higher_bid_aligns & boring_difficulty_aligns ~ "boring, difficult",
           TRUE ~ "other"
         )) %>%
  ggplot(aes(y = what_aligns)) +
  geom_bar(fill = "lightblue") +
  geom_text(stat = 'count', aes(label = ..count..), hjust = -0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  labs(x = "Count", y = "Per subject, which align? The same task is more: ")
```

## plotting betas of accuracy vs previous bid as a function of trial index

### including all trials

``` {r models}
betas <- final_df_excluded %>%
  filter(trial_count == 1) %>% # to make it one data point per participant per block
  group_by(curr_block_num) %>%
  do(tidy(lm(following_bid_z_score ~ avg_z_accuracy, data = .))) %>%
  filter(term == "avg_z_accuracy") %>%
  select(curr_block_num, estimate)

# 2. Plot the betas as a function of current block number
ggplot(betas, aes(x = curr_block_num, y = estimate)) +
  geom_line() +
  geom_point() +
  labs(title = "Betas of avg block accuracy as a function of Block Number, to predict following bid",
       x = "Current Block Number",
       y = "Beta Coefficient for z-scored block accuracy")

ggplot(betas, aes(x = curr_block_num, y = estimate)) +
  geom_point() +
  geom_smooth(method="lm",se=TRUE) +
  labs(title = "Betas of avg block accuracy as a function of Block Number, to predict following bid",
       x = "Current Block Number",
       y = "Beta Coefficient for z-scored avg block accuracy")
```

``` {r models}
betas_2 <- final_df_excluded %>%
  filter(curr_block_num != 1) %>% # to make it one data point per participant per block
  group_by(curr_block_num, game_type) %>%
  do(tidy(lm(following_bid_z_score ~ avg_block_rt + (1|subj_id), data = .))) %>%
  filter(term == "avg_block_rt") %>%
  select(curr_block_num, game_type, estimate)

# 2. Plot the betas as a function of current block number
ggplot(betas_2, aes(x = curr_block_num, y = estimate)) +
  geom_line() +
  geom_point() +
  labs(title = "Betas of avg_block_rt as a function of Block Number, to predict following bid",
       x = "Current Block Number",
       y = "Beta Coefficient for avg_block_rt")

ggplot(betas_2, aes(x = curr_block_num, y = estimate)) +
  geom_point() +
  facet_wrap(~game_type) +
  geom_smooth(method="lm",se=TRUE) +
  labs(title = "Betas of rt as a function of Block Number, to predict following bid",
       x = "Current Block Number",
       y = "Beta Coefficient for rt")
```


### including only the first trial of each block



# MODEL COMPARISON

Test different linear models for predicting bid, predicting average block accuracy, predicting individual trail accuracy, and same for RT.

``` {r single_trial_lmer_models}

complete_data <- na.omit(final_df_excluded[, c("correct", "rt","curr_block_num", "game_type", "preceding_bid", "block_switched", "subj_id", "sr_practice_accuracy", "vs_practice_accuracy", "avg_block_accuracy", "avg_block_rt", "trial_index")])

# for single trial accuracy prediction
fit.compact_st = lmer(formula = correct ~ (1 | subj_id),
                   data = complete_data)

fit.augmented_st_one = lmer(formula = correct ~ (1|subj_id) + (1|curr_block_num),
                     data = complete_data)

fit.augmented_st_two = lmer(formula = correct ~ game_type + (1|subj_id) + (1|curr_block_num),
                     data = complete_data)

fit.augmented_st_three = lmer(formula = correct ~ preceding_bid + game_type + (1|subj_id) + (1|curr_block_num),
                     data = complete_data)

fit.augmented_st_four = lmer(formula = correct ~ preceding_bid + game_type + block_switched + (1|subj_id) + (1|curr_block_num),data = complete_data)

fit.augmented_st_five = lmer(formula = correct ~ game_type + preceding_bid*block_switched + (1|subj_id) + (1|curr_block_num),data = complete_data)

fit.augmented_st_six = lmer(formula = correct ~ game_type + preceding_bid*block_switched + (1 + preceding_bid|subj_id) + (1|curr_block_num),data = complete_data) # didnt converge

fit.augmented_st_seven = lmer(formula = correct ~ game_type + preceding_bid*block_switched + (1 + preceding_bid + game_type|subj_id) + (1|curr_block_num),data = complete_data) # didnt converge

fit.augmented_st_eight = lmer(formula = correct ~ preceding_bid*block_switched + (1 + preceding_bid|subj_id) + (1|curr_block_num) + (game_type|subj_id),data = complete_data) # didnt converge

fit.augmented_st_nine = lmer(formula = correct ~ preceding_bid*block_switched + (1 + preceding_bid|subj_id) + (1|curr_block_num) + (1|game_type),data = complete_data) # didnt converge
```

Want to add preceding_bid | subj_id as random slope, and also game_type | subj_id as random slope but it doesn't converge.

``` {r models}
summary(fit.compact_st)
summary(fit.augmented_st_one)
summary(fit.augmented_st_two)
summary(fit.augmented_st_three)
summary(fit.augmented_st_four)
summary(fit.augmented_st_five)
summary(fit.augmented_st_six)
summary(fit.augmented_st_seven)
summary(fit.augmented_st_eight)
summary(fit.augmented_st_nine)
```
``` {r single_trial_lmer_models}

anova(fit.compact_st, fit.augmented_st_one) # one is better

anova(fit.augmented_st_one, fit.augmented_st_two) # two is better

anova(fit.augmented_st_two, fit.augmented_st_three) # three is better

anova(fit.augmented_st_three, fit.augmented_st_four) # four is better

anova(fit.augmented_st_four, fit.augmented_st_five) # five is better

anova(fit.augmented_st_five, fit.augmented_st_six) # six is better

anova(fit.augmented_st_six, fit.augmented_st_seven) # seven is better

anova(fit.augmented_st_seven, fit.augmented_st_eight) # unclear

anova(fit.augmented_st_six, fit.augmented_st_eight) # eight is better

anova(fit.augmented_st_eight, fit.augmented_st_nine) # eight is better

summary(fit.augmented_st_six)
summary(fit.augmented_st_seven)
summary(fit.augmented_st_eight)
```
In model 6, block_switchedtrue has a sig neg estimate but preceding_bid:block_switchedtrue has a sig positive estimate. In model 7 and model 8, these patterns are still there but the interaction is no longer significant.

``` {r block_lmer_models}
fit.augmented_st_six_edit = lmer(formula = correct ~ game_type + preceding_bid*block_switched*curr_block_num + (1 + preceding_bid|subj_id) + (1|curr_block_num),data = complete_data)

summary(fit.augmented_st_six_edit)
```


### using easy stats for this to better understand model performance
``` {r block_lmer_models}
complete_data <- na.omit(final_df_excluded[, c("correct", "rt","curr_block_num", "game_type", "preceding_bid_z_score","z_overall_correct", "preceding_bid", "block_switched", "subj_id", "sr_practice_accuracy", "vs_practice_accuracy", "avg_block_accuracy", "avg_block_rt", "trial_index")])

# do the models from before (other than the singular ones)
fit.compact_st_z = lmer(formula = z_overall_correct ~ (1|curr_block_num),
                   data = complete_data)

fit.augmented_st_one_z = lmer(formula = z_overall_correct ~ game_type + (1|curr_block_num),
                     data = complete_data)

fit.augmented_st_two_z = lmer(formula = z_overall_correct ~ preceding_bid_z_score + game_type + (1|curr_block_num),
                     data = complete_data)

fit.augmented_st_three_z = lmer(formula = z_overall_correct ~ preceding_bid_z_score + game_type + block_switched + (1|curr_block_num),
                     data = complete_data)

fit.augmented_st_four_z = lmer(formula = z_overall_correct ~ preceding_bid_z_score + game_type + block_switched + (1 + preceding_bid_z_score|curr_block_num),data = complete_data)

fit.augmented_st_five_z = lmer(formula = z_overall_correct ~ game_type + preceding_bid_z_score*block_switched + (1 + preceding_bid_z_score|curr_block_num),data = complete_data)

# Evaluate the model performance
# model_st_five_performance <- performance::check_model(fit.augmented_st_five_z)
# model_performance(fit.augmented_st_five_z)

# compare the models
compare_performance(fit.compact_st_z, fit.augmented_st_one_z, fit.augmented_st_two_z, fit.augmented_st_three_z, fit.augmented_st_four_z,  fit.augmented_st_five_z,rank = TRUE, verbose = FALSE)

summary(fit.augmented_st_five_z)
```

## block wide accuracy models
``` {r block_lmer_models}

complete_data <- (final_df_excluded[, c("curr_block_num", "game_type", "preceding_bid", "block_switched", "subj_id", "sr_practice_accuracy", "vs_practice_accuracy", "avg_block_accuracy", "avg_block_rt", "following_bid_z_score", "preceding_bid_z_score")]) %>%
  na.omit() %>%
  distinct() %>%
  arrange(subj_id, curr_block_num)
  

# for block accuracy predictions

# for single trial accuracy prediction
fit.compact_b = lmer(formula = avg_block_accuracy ~ (1 | subj_id),
                   data = complete_data)

fit.augmented_b_one = lmer(formula = avg_block_accuracy ~ (1|subj_id) + (1|curr_block_num),
                     data = complete_data)

fit.augmented_b_two = lmer(formula = avg_block_accuracy ~ game_type + (1|subj_id) + (1|curr_block_num),
                     data = complete_data)

fit.augmented_b_three = lmer(formula = avg_block_accuracy ~ preceding_bid_z_score + game_type + (1 + curr_block_num|subj_id),
                     data = complete_data) # no converge

fit.augmented_b_four = lmer(formula = avg_block_accuracy ~ preceding_bid_z_score + game_type + block_switched + (1 + curr_block_num|subj_id),data = complete_data) # no converge

fit.augmented_b_five = lmer(formula = avg_block_accuracy ~ preceding_bid_z_score*block_switched + (1 + curr_block_num|subj_id),data = complete_data)

fit.augmented_b_six = lmer(formula = avg_block_accuracy ~ preceding_bid_z_score*block_switched + (1 + curr_block_num|subj_id) + (1|game_type),data = complete_data)

fit.augmented_b_seven = lmer(formula = avg_block_accuracy ~ game_type + preceding_bid_z_score*block_switched + (1 + game_type|subj_id) + (1|curr_block_num),data = complete_data) # no converge



# compare them
anova(fit.compact_b, fit.augmented_b_one) # unclear
anova(fit.augmented_b_one, fit.augmented_b_two) # unclear
anova(fit.augmented_b_two, fit.augmented_b_three) # three is better
anova(fit.augmented_b_three, fit.augmented_b_four) # four is better
anova(fit.augmented_b_four, fit.augmented_b_five) # unclear
anova(fit.augmented_b_five, fit.augmented_b_six) # unclear
anova(fit.augmented_b_six, fit.augmented_b_seven) # seven is better
anova(fit.augmented_b_four,fit.augmented_b_seven) # seven is better
anova(fit.augmented_b_five, fit.augmented_b_seven) # seven is better
anova(fit.augmented_b_two, fit.augmented_b_seven) # seven is better
anova(fit.augmented_b_one, fit.augmented_b_seven) # seven is better
anova(fit.compact_b, fit.augmented_b_seven) # seven is better

summary(fit.augmented_b_seven)
```
Model 7 is best so far; switching blocks has a significant negative effect, but switching blocks and having a high preceding bid score had a postive effect (although non significant)


### using easy stats for this to better understand model performance
``` {r block_lmer_models}
complete_data <- na.omit(final_df_excluded[, c("curr_block_num", "game_type", "preceding_bid_z_score", "preceding_bid", "block_switched", "subj_id", "sr_practice_accuracy", "vs_practice_accuracy", "avg_block_accuracy", "avg_block_rt", "trial_index", "avg_z_accuracy", "following_bid_z_score")])%>%
  na.omit() %>%
  distinct() %>%
  arrange(subj_id, curr_block_num)

fit.compact_b_z = lmer(formula = avg_z_accuracy ~ (1 | curr_block_num),
                   data = complete_data)

fit.augmented_b_one_z = lmer(formula = avg_z_accuracy ~ game_type + (1|curr_block_num),
                     data = complete_data)

fit.augmented_b_two_z = lmer(formula = avg_z_accuracy ~ preceding_bid_z_score + game_type + (1|curr_block_num),
                     data = complete_data)

fit.augmented_b_three_z = lmer(formula = avg_z_accuracy ~ preceding_bid_z_score + game_type + (1 + preceding_bid_z_score|curr_block_num),
                     data = complete_data)

fit.augmented_b_four_z = lmer(formula = avg_z_accuracy ~ preceding_bid_z_score + game_type + block_switched + (1 + preceding_bid_z_score|curr_block_num),data = complete_data) 

fit.augmented_b_five_z = lmer(formula = avg_z_accuracy ~ preceding_bid_z_score*block_switched + (1 + preceding_bid_z_score|curr_block_num),data = complete_data)

fit.augmented_b_six_z = lmer(formula = avg_z_accuracy ~ preceding_bid_z_score*block_switched + game_type + (1+preceding_bid_z_score|curr_block_num),data = complete_data)

fit.augmented_b_seven_z = lmer(formula = avg_z_accuracy ~ game_type + preceding_bid_z_score*block_switched + (game_type|subj_id) + (1|curr_block_num),data = complete_data) 

fit.augmented_b_eight_z = lmer(formula = avg_z_accuracy ~ preceding_bid_z_score*block_switched + (game_type|subj_id) + (1|curr_block_num),data = complete_data) 

fit.augmented_b_nine_z = lmer(formula = avg_z_accuracy ~ preceding_bid_z_score*block_switched + (1|subj_id) + (1|curr_block_num),data = complete_data) 

fit.augmented_b_ten_z = lmer(formula = avg_z_accuracy ~ preceding_bid_z_score*block_switched + (1|subj_id) + (1+preceding_bid_z_score|curr_block_num),data = complete_data) 

fit.augmented_b_eleven_z = lmer(formula = avg_z_accuracy ~ preceding_bid_z_score*block_switched + (1+game_type|subj_id) + (1|curr_block_num),data = complete_data) 

# compare the models
compare_performance(fit.compact_b_z, fit.augmented_b_one_z, fit.augmented_b_two_z, fit.augmented_b_three_z, fit.augmented_b_four_z,  fit.augmented_b_five_z, fit.augmented_b_six_z, fit.augmented_b_seven_z, fit.augmented_b_eight_z, fit.augmented_b_nine_z,fit.augmented_b_ten_z,fit.augmented_b_eleven_z,rank = TRUE, verbose = FALSE)

summary(fit.augmented_b_eight_z)

summary(fit.augmented_b_eleven_z)
```

  
## factors that predict the bid

``` {r block_lmer_models}

complete_data <- (final_df_excluded[, c("curr_block_num", "correct", "game_type", "preceding_bid", "block_switched", "subj_id", "sr_practice_accuracy", "vs_practice_accuracy", "avg_block_accuracy", "avg_block_rt", "following_bid_z_score", "z_overall_correct", "avg_z_accuracy")]) %>%
  na.omit() %>%
  arrange(subj_id, curr_block_num)

# for bid predictions
fit.compact_bid = lmer(formula = following_bid_z_score ~ (1 | subj_id),
                   data = complete_data)

fit.augmented_bid_one = lmer(formula = following_bid_z_score ~ (1|curr_block_num) + (1|subj_id),
                     data = complete_data)

fit.augmented_bid_two = lmer(formula = following_bid_z_score ~ game_type + (1|subj_id) + (1|curr_block_num),
                     data = complete_data)

fit.augmented_bid_three = lmer(formula = following_bid_z_score ~ (1 + game_type|subj_id) + (1|curr_block_num),
                     data = complete_data)

fit.augmented_bid_four = lmer(formula = following_bid_z_score ~ z_overall_correct + (1 + game_type|subj_id) + (1|curr_block_num),
                     data = complete_data)

fit.augmented_bid_five = lmer(formula = following_bid_z_score ~ z_overall_correct + (1 + game_type|subj_id) + (1|curr_block_num) + (1|block_switched),
                     data = complete_data)

fit.augmented_bid_six = lmer(formula = following_bid_z_score ~ avg_z_accuracy + (1 + game_type|subj_id) + (1|curr_block_num) + (1|block_switched),
                     data = complete_data)

compare_performance(fit.compact_bid, fit.augmented_bid_one, fit.augmented_bid_two, fit.augmented_bid_three, fit.augmented_bid_four, fit.augmented_bid_five,fit.augmented_bid_six, rank = TRUE, verbose = FALSE)

summary(fit.augmented_bid_five)
summary(fit.augmented_bid_six)

```

