---
title: "pilotB_analysis_7to21"
output: html_document
date: "2024-06-01"
---
This is the analysis on the preliminary pilot B data (from friends). Pre FYP.

The setup was:
8 spatial recall practice
16 visual search practice
10 blocks
- 16 visual search per block
- 8 spatial recall per block

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
##library(jsonlite)
library("broom")      # for tidying up linear models 
library("car")        # for running ANOVAs
library("afex")       # also for running ANOVAs
library("emmeans")    # for calculating constrasts

# set the default ggplot theme 
theme_set(theme_classic())
```

**reading in the data**
``` {r data_wrangling}
setwd("../../data/pilotB/")

csv_files <- list.files(pattern = "\\.csv$")

# Function to read a CSV file and convert all columns to character type
read_csv_as_character <- function(file) {
  df <- read.csv(file, stringsAsFactors = FALSE)
  df[] <- lapply(df, as.character)
  return(df)
}

# Will wrangle each participant's data independently to see details of their runs
df_13 <- bind_rows(lapply(csv_files[1],read_csv_as_character)) ## 7
df_15 <- bind_rows(lapply(csv_files[2],read_csv_as_character)) ## 11
df_16 <- bind_rows(lapply(csv_files[3],read_csv_as_character)) ## 13
df_18 <- bind_rows(lapply(csv_files[4],read_csv_as_character)) ## 14
df_19 <- bind_rows(lapply(csv_files[5],read_csv_as_character)) ## 21
## lATER JUST BIND THEM ALL, no need to do it this way (since you're no longer debugging)

# df_21 <- bind_rows(lapply(csv_files[6],read_csv_as_character))
# df_22 <- bind_rows(lapply(csv_files[7],read_csv_as_character))
```
**pre-processing the data**
First I will anonymize the data and remove unneccesary columns:
``` {r data_wrangling}
anonymize_clean <- function(df) {
  df <- df %>%
    select(-recorded_at,-ip,-user_agent,-referer,-sequence_length,
         -accept_language,-device,-internal_node_id,-view_history,
         -source_code_version, -contains("browser"),-contains("platform"),
         -contains("screen"),-contains("width"),-contains("height"),
         -contains("failed"),-condition,-success,-event_history)
  return(df)
}
# df_list <-  list(df_13,df_15,df_16,df_18,df_19,df_21,df_22)
# df_list <- lapply(df_list, anonymize_clean)
df_13 <- anonymize_clean(df_13)
df_15 <- anonymize_clean(df_15)
df_16 <- anonymize_clean(df_16)
df_18 <- anonymize_clean(df_18)
df_19 <- anonymize_clean(df_19)
# df_21 <- anonymize_clean(df_21)
# df_22 <- anonymize_clean(df_22)
```

Now I will take out the practice trials and save them to a different df, I will also remove practice and all other trial types (other than sr or vs) from my dataframe
``` {r data_wrangling}
save_practice <- function(df1, df2, df3, df4, df5) {
  practice_list <- list(df1, df2, df3, df4, df5)

  for (i in seq_along(practice_list)) {
    practice_list[[i]] <- practice_list[[i]] %>%
      filter(practice == "true")
  }

  return(practice_list)
}

practice_runs_df <- save_practice(df_13,df_15,df_16,df_18,df_19)


# remove irrelevant rows from main analysis dfs
# parse bid values
remove_non_game <- function(df) {
  df <- df %>%
    filter(trial_type != "instructions", trial_type != "preload", 
           trial_type != "survey-multi-choice",
           (trial_type != 'html-keyboard-response' | trial_id =='test_trial'),
           (trial_type != 'html-button-response'),
           !grepl("screen", trial_type, ignore.case = TRUE)) %>%
    filter(practice != "true") %>%
    mutate(bid_value = as.integer(gsub("[^0-9]+", "", response))) 
  
  return(df)
}

df_13_sub <- remove_non_game(df_13)
df_15_sub <- remove_non_game(df_15)
df_16_sub <- remove_non_game(df_16)
df_18_sub <- remove_non_game(df_18)
df_19_sub <- remove_non_game(df_19)
# df_21_sub <- remove_non_game(df_21)
# df_22_sub <- remove_non_game(df_22)
```

Now I'm going to distribute the bid value to its corresponding block for each df. I will also record which block each group of trials is, remove unneccary columns, and change the datatypes of necessary columns (i.e. subject id).
``` {r data_wrangling}
# spread bid and blocks completed value onto the entire block
# this new column will be how much the participant bid 
bid_val_dev <- function(df) {
  sr_practice_num <- 8
  sr_per_block <- 8
  vs_practice_num <- 16
  vs_per_block <- 16
  num_blocks <- 10
  
  df_test <- df
  
  # get run id of current df
  run_id = df$run_id[[1]]
  
  # spatial recall
  sr <- df_test %>%
    filter((prevBlockType == "spatial_recall" & 
                                switch_next_block == "false") |
                      (prevBlockType == "vs" & switch_next_block == "true")
         | (game_type == "spatial_recall"))

  if (nrow(sr) > 0 && sr$trial_type[1] != "survey-text"){
    print("adding sr row")
    sr <- sr %>% add_row(blocks_completed = '0', trial_type = 'survey-text',run_id = as.character(run_id), .before = 0)
  }
  
  sr <- sr %>%
    mutate(switch_next_block = ifelse(switch_next_block == "", NA, switch_next_block),group = rep(1:(n() %/% (sr_per_block + 1) + 1), each = (sr_per_block + 1), length.out = n())) %>%
    group_by(group) %>%
    mutate(switch_next_block = as.character(switch_next_block)) %>%
    fill(bid_value, switch_next_block,blocks_completed, .direction = "down") %>%
    ungroup() %>%
    select(-group,-bonus,-overall_accuracy,-score_pc,-score_ls)
  
  # visual search
  vs <- df_test %>%
    filter((prevBlockType == "vs" & 
                                  switch_next_block == "false") |
                        (prevBlockType == "spatial_recall" & switch_next_block == "true")
           | (game_type == "vs")) %>%
    arrange(trial_index)

  if (nrow(vs) > 0 && vs$trial_type[1] != "survey-text"){
    print("adding vs row")
    vs <- vs %>% add_row(blocks_completed = '0', trial_type = 'survey-text', run_id = as.character(run_id), .before = 0, trial_index = '0')
  }

  vs <- vs %>%
    mutate(switch_next_block = ifelse(switch_next_block == "", NA, switch_next_block),group = rep(1:(n() %/% (vs_per_block + 1) + 1), each = (vs_per_block + 1), length.out = n())) %>%
    group_by(group) %>%
    mutate(switch_next_block = as.character(switch_next_block)) %>%
    fill(bid_value, switch_next_block,blocks_completed, .direction = "down")%>%
    ungroup() %>%
    select(-group,-bonus,-overall_accuracy,-score_pc,-score_ls)
  
  final_df <- bind_rows(sr,vs)
  
  return(final_df)
}
df_13_sub <- bid_val_dev(df_13_sub) %>% arrange(trial_index)
df_15_sub <- bid_val_dev(df_15_sub) %>% arrange(trial_index)
df_16_sub <- bid_val_dev(df_16_sub) %>% arrange(trial_index)
df_18_sub <- bid_val_dev(df_18_sub) %>% arrange(trial_index)
df_19_sub <- bid_val_dev(df_19_sub) %>% arrange(trial_index)
# df_21_sub <- bid_val_dev(df_21_sub)
# df_22_sub <- bid_val_dev(df_22_sub)

```

``` {r data_wrangling}
# assign block numbers
block_num_parse_vals <- function(df) {
  df <- df %>%
    mutate(subj_id = as.numeric(run_id), blocks_completed = as.numeric(blocks_completed,na.RM = TRUE)) %>%
    select(-run_id,-generated_BDM_value,-question_order) %>%
    mutate(curr_block_num = blocks_completed + 1) 
  
  return(df)
}
df_13_sub <- block_num_parse_vals(df_13_sub)
df_15_sub <- block_num_parse_vals(df_15_sub)
df_16_sub <- block_num_parse_vals(df_16_sub)
df_18_sub <- block_num_parse_vals(df_18_sub)
df_19_sub <- block_num_parse_vals(df_19_sub)
# df_21_sub <- block_num_parse_vals(df_21_sub)
# df_22_sub <- block_num_parse_vals(df_22_sub)
```

Now I will combine all of the participants cleaned data into one df, and will calculate average accuracy per block, average bid offer, stdev of bid offers,
z-score per bid offer. I also wanted to make a column for following_bid (the bid that followed a block)
``` {r data_wrangling}
total_data <- bind_rows(df_13_sub,df_15_sub,df_16_sub,df_18_sub,df_19_sub) %>%
  # filter(trial_type != "survey-text") %>%
  arrange(subj_id, curr_block_num) %>%
  rename(preceding_bid = bid_value)

bid_vals <- total_data %>%
  filter(trial_type == "survey-text") %>%
  group_by(subj_id) %>%
  arrange(subj_id,blocks_completed) %>%
  mutate(following_bid = lead(preceding_bid))

total_data <- total_data %>%
  left_join(bid_vals %>% select(subj_id, curr_block_num, following_bid),
            by = c("subj_id","curr_block_num"))
```

``` {r data_wrangling}
# get average bids per participant
avg_subj_bids <- total_data %>%
  filter(trial_type == "survey-text") %>%
  group_by(subj_id) %>%
  summarise(avg_bids = mean(preceding_bid,na.rm = TRUE),stdev_bids = sd(preceding_bid, na.rm = TRUE)) %>%
  ungroup()
total_data <- total_data %>%
  left_join(avg_subj_bids, by = "subj_id")

# make a column that represents how different (in stdev) the amount they want to switch is from their mean
total_data <- total_data %>%
  mutate(preceding_bid_z_score = if_else(stdev_bids == 0, 0, 
                                         ifelse(is.na(preceding_bid),0,
                                                ((preceding_bid - avg_bids) / 
                                                   stdev_bids))),
         following_bid_z_score = if_else(stdev_bids == 0, 0, 
                                         ifelse(is.na(following_bid),0,
                                                ((following_bid - avg_bids) / stdev_bids)))) %>%
  filter(trial_type != "survey-text") %>%
  select(-time_elapsed,-response,-sequence,-fbclid, -trial_id, -choices, -ITIParams, -num_stimuli,-correct_response, -missed_response,-backwards,-responses,-practice,-prevBlockType,
         -preceding_bid,-following_bid,-avg_bids,-stdev_bids) %>%
  rename(block_switched=switch_next_block)
```

Now I will calculate average accuracy per block.
``` {r data_wrangling}
# conversion dict leftover
conversion <- c("true" = 1, "false" = 0)

avg_spatial_recall <- total_data %>%
  filter(game_type == "spatial_recall") %>%
  group_by(subj_id, curr_block_num) %>%
  summarise(avg_accuracy = mean(as.numeric(score_an), na.rm = TRUE),stdev_accuracy = sd(as.numeric(score_an),na.rm = TRUE))%>%
  arrange(subj_id,curr_block_num)

avg_vs <- total_data %>%
  filter(game_type == "vs") %>%
  group_by(subj_id, curr_block_num) %>%
  summarise(avg_accuracy = mean(as.numeric(correct_trial), na.rm = TRUE),stdev_accuracy = sd(as.numeric(correct_trial),na.rm=TRUE))

avg_per_block <- bind_rows(avg_spatial_recall, avg_vs) %>%
  arrange(subj_id, curr_block_num)
```

Now I will join these values into my total dataset.
``` {r data_wrangling}
total_data <- total_data %>%
  left_join(avg_per_block, by = c("subj_id","curr_block_num"))
```

**analyzing and plotting the data**

Plotting bids over time:
``` {r data_wrangling}
bid_block_total <- total_data %>%
  select(subj_id,curr_block_num,blocks_completed,following_bid_z_score,
         preceding_bid_z_score,avg_accuracy,stdev_accuracy) %>%
  group_by(subj_id,curr_block_num,blocks_completed,avg_accuracy,stdev_accuracy) %>%
  summarise(avg_following_bid_z = mean(following_bid_z_score),
            avg_preceding_bid_z = mean(preceding_bid_z_score))

# faceted by subject
bid_block_total %>%
  mutate(subj_id = as.factor(subj_id)) %>%
  ggplot(mapping = aes(x=curr_block_num,y=avg_following_bid_z,fill=subj_id,color=subj_id)) +
  geom_point(alpha = 0.3,
             position = position_jitter(height = 0, width = 0.1)) +
  facet_wrap(~subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  labs(x = "Block number", 
       y = "Z-scored bid offer (relative to each subject's avg and sd)", 
       title = "Bid offers following each block, by subject")

# not faceted by subject
bid_block_total %>%
  mutate(subj_id = as.factor(subj_id)) %>%
  group_by(curr_block_num) %>%
  ggplot(mapping = aes(x=curr_block_num,y=avg_following_bid_z,fill=subj_id,color=subj_id)) +
  geom_point(alpha = 0.3,
             position = position_jitter(height = 0, width = 0.1)) +
  geom_smooth(method="lm",se=TRUE) +
  labs(x = "Block number", 
       y = "Z-scored bid offer (relative to each subject's avg and sd)", 
       title = "Bid offers following each block, by subject")

# averaged across all participants
bid_block_total %>%
  group_by(curr_block_num) %>%
  ggplot(mapping = aes(x=curr_block_num,y=avg_following_bid_z)) +
  geom_point(alpha = 0.3,
             position = position_jitter(height = 0, width = 0.1)) +
  geom_smooth(method="lm",se=TRUE) +
  labs(x = "Block number", 
       y = "Z-scored bid offer (relative to each subject's avg and sd)", 
       title = "Bid offers following each block, by subject")
```

Plotting preceding bid by avg accuracy in following block:
``` {r data_wrangling}
# including all subjects
bid_block_total %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x = avg_preceding_bid_z, y = avg_accuracy)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 3) +  # Points colored by block number
  labs(x = "Preeding Bid Z-Score",
       y = "Average Accuracy in Next Block",
       color = "Block Number") +
  ggtitle("Bid Z-Score by Following Average Accuracy for Each Block, across subjects")

# faceted by subjects
bid_block_total %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x = avg_preceding_bid_z, y = avg_accuracy)) +
  facet_wrap(~subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 3) +  # Points colored by block number
  labs(x = "Preceding Bid Z-Score",
       y = "Average Accuracy",
       color = "Block Number") +
  ggtitle("Bid Z-Score by Following Average Accuracy for Each Block, across subjects")
```
Plotting following bid by avg accuracy in a block:

``` {r data_wrangling}
# including all subjects
bid_block_total %>%
  ggplot(mapping = aes(x = avg_following_bid_z, y = avg_accuracy)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 3) +  # Points colored by block number
  labs(x = "Following Bid Z-Score",
       y = "Average Accuracy",
       color = "Block Number") +
  ggtitle("Average Accuracy by Following Bid Z-Score for Each Block, across subjects")

# faceted by subjects
bid_block_total %>%
  ggplot(mapping = aes(x = avg_following_bid_z, y = avg_accuracy)) +
  facet_wrap(~subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = curr_block_num), size = 3) +  # Points colored by block number
  labs(x = "Following Bid Z-Score",
       y = "Average Accuracy",
       color = "Block Number") +
  ggtitle("Average Accuracy by Following Bid Z-Score for Each Block, by subject")

```
Plotting avg accuracies in spatial recall vs vs:

``` {r data_wrangling}
conversion_switch <- c("true" = 1, "false" = 0)
bid_block_total_details <- total_data %>%
  select(subj_id,curr_block_num,blocks_completed,following_bid_z_score,
         preceding_bid_z_score,avg_accuracy,stdev_accuracy,game_type,block_switched) %>%
  group_by(subj_id,curr_block_num,blocks_completed,avg_accuracy,stdev_accuracy,block_switched,game_type) %>%
  summarise(avg_following_bid_z = mean(following_bid_z_score),
            avg_preceding_bid_z = mean(preceding_bid_z_score)) %>%
  mutate(block_switched = ifelse(is.na(block_switched),0,conversion_switch[block_switched])) %>%
  arrange(subj_id, curr_block_num)
```

``` {r data_wrangling}
total_data %>%
  filter(game_type == "spatial_recall") %>%
  mutate(subj_id = as.factor(subj_id),score_an = as.numeric(score_an)) %>%
  arrange(trial_index) %>%
  ggplot(mapping = aes(x = curr_block_num,y=score_an,fill=subj_id,color=subj_id)) +
  facet_wrap(~subj_id,ncol=2) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(alpha = 0.4,
             position = position_jitter(width = 0.3,
                                        height = 0),
             size = 2) +
  labs(x = "Block number (arranged by trial_index)",
       y = "Accuracy per trial") +
  ggtitle("Spatial Recall: Accuracy over trials, by subject")

total_data %>%
  filter(game_type == "vs") %>%
  mutate(subj_id = as.factor(subj_id),correct = as.numeric(correct_trial)) %>%
  arrange(trial_index) %>%
  ggplot(mapping = aes(x = curr_block_num,y=correct,fill=subj_id,color=subj_id)) +
  facet_wrap(~subj_id,ncol=2) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(alpha = 0.4,
             position = position_jitter(width = 0.3,
                                        height = 0),
             size = 2) +
  labs(x = "Block number (arranged by trial_index)",
       y = "Accuracy per trial") +
  ggtitle("VS: Accuracy over trials, by subject")

```

``` {r data_wrangling}
bid_block_total_details %>%
  filter(game_type == "vs") %>%
  mutate(subj_id = as.factor(subj_id)) %>%
  group_by(curr_block_num) %>%
  ggplot(mapping = aes(x = curr_block_num, y = avg_accuracy)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = subj_id), size = 3) +  # Points colored by block number
  labs(x = "Block number",
       y = "Average Accuracy") +
  ggtitle("VS: Average Accuracy for Each Block, across subjects")

bid_block_total_details %>%
  filter(game_type == "spatial_recall") %>%
  mutate(subj_id = as.factor(subj_id)) %>%
  group_by(curr_block_num) %>%
  ggplot(mapping = aes(x = curr_block_num, y = avg_accuracy)) +
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = subj_id), size = 3) +  # Points colored by block number
  labs(x = "Block number",
       y = "Average Accuracy") +
  ggtitle("Spatial Recall: Average Accuracy for Each Block, across subjects")
```

By subject:

``` {r data_wrangling}
bid_block_total_details %>%
  filter(game_type == "vs") %>%
  mutate(subj_id = as.factor(subj_id)) %>%
  group_by(curr_block_num) %>%
  ggplot(mapping = aes(x = curr_block_num, y = avg_accuracy)) +
  facet_wrap(~subj_id) + 
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = subj_id), size = 3) +  # Points colored by block number
  labs(x = "Block number",
       y = "Average Accuracy") +
  ggtitle("VS: Average Accuracy for Each Block, by subjects")

bid_block_total_details %>%
  filter(game_type == "spatial_recall") %>%
  mutate(subj_id = as.factor(subj_id)) %>%
  group_by(curr_block_num) %>%
  ggplot(mapping = aes(x = curr_block_num, y = avg_accuracy)) +
  facet_wrap(~subj_id) + 
  geom_smooth(method="lm",se=TRUE) +
  geom_point(mapping = aes(color = subj_id), size = 3) +  # Points colored by block number
  labs(x = "Block number",
       y = "Average Accuracy") +
  ggtitle("Spatial Recall: Average Accuracy for Each Block, by subjects")
```

Looking at overall average accuracy in spatial recall vs in vs, by subject
``` {r data_wrangling}
total_data %>%
  mutate(subj_id = as.factor(subj_id),score_an = as.numeric(score_an),
         correct = conversion_switch[correct]) %>%
  mutate(correct_total = ifelse(game_type == "spatial_recall",score_an,as.numeric(correct_trial)),
         block_switched = ifelse(is.na(block_switched),"block did not switch", ifelse(block_switched == 0,"block did not switch","block switched"))) %>%
  group_by(subj_id) %>%
  ggplot(mapping = aes(x=game_type,y=correct_total)) +
  facet_wrap(~block_switched) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.4,
                                        height = 0.01)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1) +
  labs(x="task type",y="accuracy per trial per subject")+
  ggtitle("Trial accuracy by task type")

bid_block_total_details %>%
  mutate(subj_id = as.factor(subj_id),block_switched = ifelse(is.na(block_switched),"block did not switch", ifelse(block_switched == 0,"block did not switch","block switched"))) %>%
  ggplot(mapping = aes(x=game_type,y=avg_accuracy,color=subj_id)) +
  facet_wrap(~block_switched) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.4,
                                        height = 0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1) +
  labs(x="task type",y="average accuracy per block per subject")+
  ggtitle("Block accuracy by task type, across subjects")

bid_block_total_details %>%
  mutate(subj_id = as.factor(subj_id),block_switched = ifelse(is.na(block_switched),"block did not switch", ifelse(block_switched == 0,"block did not switch","block switched"))) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_accuracy,color=subj_id)) +
  facet_wrap(~game_type) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.4,
                                        height = 0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1) +
  labs(x="Is this a switched task",y="average accuracy per block per subject")+
  ggtitle("Block accuracy by task type, across subjects")
```
Bid offers by switch or not
``` {r data_wrangling}
bid_block_total_details %>%
  mutate(subj_id = as.factor(subj_id),block_switched = ifelse(is.na(block_switched),"block did not switch", ifelse(block_switched == 0,"block did not switch","block switched"))) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_following_bid_z,color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  facet_wrap(~game_type)+
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  labs(x="Did the task switch this block?",y="Average bid by participant/block after this block")+
  ggtitle("Relationship between switch status and following bid offer")

```
Do mixed effects models/more plots to test and look at:
- does bid offer predict future accuracy
- if bid offer is in higher bucket, and switch was successful vs unsucessful, how does that change accuracy? (accounting for game type)
- does successful switching predict future accuracy
- does accuracy predict bid offer
- how does all of this differ by game_type
``` {r data_wrangling}
# to try to visualize this question: if bid offer is in higher bucket, and switch was successful vs unsucessful, how does that change accuracy? (accounting for game type)
breaks <- c(-Inf, -1, 0, 1, Inf)
labels <- c('more than 2 sd below', '0 to 1 sd below', '0 to 1 sd above', 'more than 1 sd above')

bid_block_total_details_binned <- bid_block_total_details %>%
  mutate(bid_bin_preceding = cut(avg_preceding_bid_z, breaks = breaks, labels = labels, right = FALSE),
         bid_bin_following = cut(avg_following_bid_z, breaks = breaks, labels = labels, right = FALSE))%>%
  mutate(subj_id = as.factor(subj_id),block_switched = ifelse(is.na(block_switched),"block did not switch", ifelse(block_switched == 0,"switch","no switch"))) %>%
  mutate(subj_id = as.factor(subj_id))

bid_block_total_details_binned %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x=block_switched,y=avg_accuracy,color=subj_id)) +
  facet_wrap(~bid_bin_preceding,ncol=4) +
  theme(panel.spacing.x = unit(2, "lines"))+
  geom_point(alpha=0.5,position = position_jitter(width=0.2,height=0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 0.5)+
  labs(x="Did the task switch?",y="Average accuracy in this block")+
  ggtitle("Relationship between bid offer, switch status and following average accuracy")
```

``` {r data_wrangling}
bid_block_total_details_binned %>%
  group_by(block_switched) %>%
  filter(curr_block_num != 1) %>%
  ggplot(mapping = aes(x=avg_preceding_bid_z,y=avg_accuracy, color = block_switched)) +
  geom_point(alpha = 0.5)+
  geom_smooth(method="lm",se=TRUE)
```

calculating overall averages per task: 
``` {r data_wrangling}
all_avgs <- total_data %>%
  mutate(correct_val = ifelse(game_type == "vs",as.numeric(correct_trial),as.numeric(score_an))) %>%
  select(subj_id,game_type, correct_val) %>%
  group_by(subj_id,game_type) %>%
  summarize(overall_game_avg = mean(correct_val))

all_avgs %>%
  ggplot(mapping = aes(x=game_type, y=overall_game_avg)) +
  geom_point(aes(x=game_type, y=overall_game_avg)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game Type",y="Average accuracy on all trials of this game, per subject")+
  ggtitle("Average of subject mean performance on each game")

```