---
title: "basic_modeling"
output: html_document
date: "2025-01-20"
---
This is the initial modeling analyses for study 2.

The setup was:
4 spatial recall practice
4 digit span practice
4 rest practice

10 groups, 13 blocks per group
- 10 digit span per block
- 10 visual search per block
- up to 20 rest per rest period

group ordering: ABABBABAAB

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("broom")      # for tidying up linear models 
library("car")        # for running ANOVAs
library("afex")       # also for running ANOVAs
library("emmeans")    # for calculating constrasts
library(jsonlite)

# set the default ggplot theme 
theme_set(theme_classic())
```

# READ IN DATA (these are all post-exclusion files from both batches)
``` {r data_wrangling}
# exp vars
sr_practice_num <- 4
sr_per_block <- 10
ds_practice_num <- 4
ds_per_block <- 10
rt_practice_num <- 4
rt_per__block_max <- 20
num_groups <- 10
num_blocks_per_group <- 3
num_blocks_overall <- num_groups * num_blocks_per_group

df_all <- read.csv("/Users/nastasiaklevak/Desktop/FYP_2024/CognitiveFatigue_TaskSpecificity/data_anonymized/SPRmain/excluded/SPRmain_main_trials_cleaned.csv",stringsAsFactors = FALSE)
df_practice <- read.csv("/Users/nastasiaklevak/Desktop/FYP_2024/CognitiveFatigue_TaskSpecificity/data_anonymized/SPRmain/excluded/SPRmain_practice_trials_cleaned.csv",stringsAsFactors = FALSE)
df_survey <- read.csv("/Users/nastasiaklevak/Desktop/FYP_2024/CognitiveFatigue_TaskSpecificity/data_anonymized/SPRmain/excluded/SPRmain_survey_cleaned.csv", stringsAsFactors = FALSE)
```

# QUESTION 1:
1) Is there a post-error increase in fatigue? i.e. is accuracy a significant negative estimator for subsequent rest time?





# QUESTION 2:
2) When does task switching reduce fatigue, if ever? i.e. how does performance differ in the block following a switch vs a non-switch, and how long is the subsequent self-paced rest (in comparison)



# QUESTION 3:
3) Is task switching acted upon as rejuvenating? i.e. will rest time when cued that the next block will be a switch be less than when cued the next block will be a stay

