---
title: "1_wrangling_HMM_data"
output: html_document
date: "2025-07-07"
---
Do data wrangling to create a dataset to feed into HMM fitting in step 2 *insert filename*. 

This is using data from the Study2_SPR experiment (anonymized data located in ../data_anonymized/SPRmain)

Format of data after this wrangling:

84 subjects
subject_data = {
    '1': {
        'epoch_accuracy': [0.8, 0.7, 0.9, ...],  # 30 values (one value per block)
        'post_epoch_post_cue_rest_duration': [2.1, 3.5, 1.8, ...],  # 30 values (one value per block)
        'rest_cue_type': ['switch' or 'stay'] # if the cue before the rest period was switch or stay (basically this is the same as epoch_follows_task_switch but one row up)
        'epoch_follows_task_switch': [1 if switch, 0 if stay], # if this block was a product of a task switch (first row has to be NA because it was neither)
        'block_number': [1,1,1, 2,2,2, 3,3,3, ..., 10,10,10],
        'epoch_within_block': [1,2,3, 1,2,3, 1,2,3, ..., 1,2,3],
        'overall_epoch': [1,2,3,4,5,6,7,8,9, ..., 28,29,30],
        'game_type': ['A','A','A', 'B','B','B', ...],
        'pre_epoch_rest_duration': [previous rest duration for each epoch] # first row has to be NA because there was no previous rest duration
    },
    # ... for all 84 subjects
}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("broom")      # for tidying up linear models 
library("car")        # for running ANOVAs
library("afex")       # also for running ANOVAs
library("emmeans")    # for calculating constrasts
library(jsonlite)
library(MASS, exclude = "select")
library(performance)
library(DHARMa)
library(effects)
library(rstatix, exclude="filter")  # For statistical tests
library(ggpubr)
library(patchwork)  # For combining plots
library(broom.mixed)
library(effects)
library(emmeans)
library(report)


# set the default ggplot theme 
theme_set(theme_classic())
```


# READ IN DATA (these are all post-exclusion files from both batches)
``` {r data_loading}
# exp vars
sr_practice_num <- 4
sr_per_block <- 10
ds_practice_num <- 4
ds_per_block <- 10
rt_practice_num <- 4
rt_per__block_max <- 20
all_per_block <- 10
num_groups <- 10
num_blocks_per_group <- 3
num_blocks_overall <- num_groups * num_blocks_per_group

df_all <- read.csv("/Users/nastasiaklevak/Desktop/FYP_2024/CognitiveFatigue_TaskSpecificity/data_anonymized/SPRmain/excluded/SPRmain_main_trials_cleaned.csv",stringsAsFactors = FALSE) %>%
  select(-X)
df_practice <- read.csv("/Users/nastasiaklevak/Desktop/FYP_2024/CognitiveFatigue_TaskSpecificity/data_anonymized/SPRmain/excluded/SPRmain_practice_trials_cleaned.csv",stringsAsFactors = FALSE)%>%
  select(-X)
df_survey <- read.csv("/Users/nastasiaklevak/Desktop/FYP_2024/CognitiveFatigue_TaskSpecificity/data_anonymized/SPRmain/excluded/SPRmain_survey_cleaned.csv", stringsAsFactors = FALSE)%>%
  select(-X)
```

``` {r data_loading}
# get average per block per subject
rest_info <- df_all %>%
  group_by(subj_id) %>%
  filter(!is.na(rest_chunk), !is.na(type_desc)) %>%
  select(subj_id, block_num = rest_chunk, num_rest_in_chunk, rest_type = type_desc) %>%
  distinct() %>%
  ungroup() %>%
  group_by(subj_id,block_num) %>%
  slice(1)  # Take only the first row for each block

# Then join with summary
df_all_blockwise <- df_all %>%
  ungroup() %>%
  filter(trial_type != "rt_main_trials") %>%
  group_by(subj_id, block_num) %>%
  summarize(
    avg_block_accuracy = mean(is_correct_numeric),
    accuracy_sd = sd(is_correct_numeric),
    avg_rt = mean(rt[!timed_out]),
    rt_sd = sd(rt[!timed_out]),
    group_num = first(group_num),
    gameA_isSR = first(gameA_isSR),
    game_type = first(game_type),
    .groups = 'drop'
  ) %>%
  left_join(rest_info, by = c("subj_id","block_num"))%>%
  mutate(cue_type = ifelse(rest_type == "block_same_same" | rest_type == "group_A_A" | rest_type == "group_B_B", "stay", "switch"))

df_all_blockwise <- df_all_blockwise %>%
  ungroup() %>%
  group_by(subj_id) %>%
  mutate(scale_rest = as.vector(scale(num_rest_in_chunk, center = TRUE, scale = TRUE)),
         scale_accuracy = as.vector(scale(avg_block_accuracy, center = TRUE, scale = TRUE))) %>%
  ungroup()

# just a check to make sure it has all non-excluded participants (84)
df_all_blockwise %>%
  select(subj_id) %>%
  distinct()
```


``` {r data_loading}
df_all_blockwise_HMM <- df_all_blockwise %>%
  group_by(subj_id) %>%
  arrange(subj_id, block_num) %>%
  mutate(post_cue_avg_accuracy = lead(avg_block_accuracy, default = NA),
         scaled_post_cue_avg_accuracy = lead(scale_accuracy, default = NA),
         following_block_rest = lead(num_rest_in_chunk, default=NA),
         scaled_following_block_rest = lead(scale_rest, default = NA)) %>%
  ungroup()
```

# wrangle data so that it's read for the first run of the heirarchical HMM file

Format of data after this wrangling:

84 subjects
subject_data = {
    '1': {
        'epoch_accuracy': [0.8, 0.7, 0.9, ...],  # 30 values (one value per block)
        'post_epoch_post_cue_rest_duration': [2.1, 3.5, 1.8, ...],  # 30 values (one value per block)
        'rest_cue_type': ['switch' or 'stay'] # if the cue before the rest period was switch or stay (basically this is the same as epoch_follows_task_switch but one row up)
        'epoch_follows_task_switch': [1 if switch, 0 if stay], # if this block was a product of a task switch (first row has to be NA because it was neither)
        'block_number': [1,1,1, 2,2,2, 3,3,3, ..., 10,10,10],
        'epoch_within_block': [1,2,3, 1,2,3, 1,2,3, ..., 1,2,3],
        'overall_epoch': [1,2,3,4,5,6,7,8,9, ..., 28,29,30],
        'game_type': ['A','A','A', 'B','B','B', ...],
        'pre_epoch_rest_duration': [previous rest duration for each epoch] # first row has to be NA because there was no previous rest duration
    },
    # ... for all 84 subjects
}

``` {r data_HMM_wrangling}
df_all_blockwise_HMM_all <- df_all_blockwise_HMM %>%
  group_by(subj_id) %>%  # Group by subject to ensure lag works within each subject
  mutate(overall_epoch = block_num,
         epoch_accuracy = avg_block_accuracy,
         post_epoch_post_cue_rest_duration = num_rest_in_chunk,
         rest_cue_type = ifelse(cue_type == "switch", 1, 0),
         epoch_follows_task_switch = ifelse(lag(cue_type) == "switch", 1, 0), # takes the previous epoch's cue_type per subj
         block_number = ceiling(overall_epoch / 3),
         epoch_within_block =  ((overall_epoch - 1) %% 3) + 1,
         pre_epoch_rest_duration = lag(post_epoch_post_cue_rest_duration)) %>% # takes previous row's rest duration
  ungroup() %>%
  select(subj_id, overall_epoch, epoch_accuracy, post_epoch_post_cue_rest_duration, rest_cue_type, 
         epoch_follows_task_switch, block_number, epoch_within_block, game_type, pre_epoch_rest_duration) %>%
  arrange(subj_id, overall_epoch)
```

## save to json file

``` {r data_saving}
# Convert to nested list structure
subject_data <- df_all_blockwise_HMM_all %>%
  group_by(subj_id) %>%
  summarise(
    epoch_accuracy = list(epoch_accuracy),
    post_epoch_post_cue_rest_duration = list(post_epoch_post_cue_rest_duration),
    rest_cue_type = list(rest_cue_type),
    epoch_follows_task_switch = list(epoch_follows_task_switch),
    block_number = list(block_number),
    epoch_within_block = list(epoch_within_block),
    overall_epoch = list(overall_epoch),
    game_type = list(game_type),
    pre_epoch_rest_duration = list(pre_epoch_rest_duration),
    .groups = 'drop'
  ) %>%
  # Convert to named list with subject IDs as keys
  {
    result <- list()
    for(i in 1:nrow(.)) {
      subj_id <- as.character(.$subj_id[i])
      result[[subj_id]] <- list(
        epoch_accuracy = .$epoch_accuracy[[i]],
        post_epoch_post_cue_rest_duration = .$post_epoch_post_cue_rest_duration[[i]],
        rest_cue_type = .$rest_cue_type[[i]],
        epoch_follows_task_switch = .$epoch_follows_task_switch[[i]],
        block_number = .$block_number[[i]],
        epoch_within_block = .$epoch_within_block[[i]],
        overall_epoch = .$overall_epoch[[i]],
        game_type = .$game_type[[i]],
        pre_epoch_rest_duration = .$pre_epoch_rest_duration[[i]]
      )
    }
    result
  }
```

``` {r data_saving}
# Save as JSON file
write_json(subject_data, "subject_data_for_HMM.json", pretty = TRUE)
```
