---
title: "pilotA_analysis_16to22"
output: html_document
date: "2024-05-20"
---
This is the analysis on the preliminary pilot A data (from friends), before the addition of a progress bar and when the spatial recall task was 5 digits to mem instead of 4. Also this gradcpt had a glitch in it (the same order of images repeated every block)

The setup was:
6 spatial recall practice
30 gradcpt practice
8 blocks
- 40 gradcpt per block
- 6 spatial recall per block

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
##library(jsonlite)
library("broom")      # for tidying up linear models 
library("car")        # for running ANOVAs
library("afex")       # also for running ANOVAs
library("emmeans")    # for calculating constrasts

# set the default ggplot theme 
theme_set(theme_classic())
```

**reading in the data**
``` {r data_wrangling}
setwd("../../data/pilotA/")

csv_files <- list.files(pattern = "\\.csv$")

# Function to read a CSV file and convert all columns to character type
read_csv_as_character <- function(file) {
  df <- read.csv(file, stringsAsFactors = FALSE)
  df[] <- lapply(df, as.character)
  return(df)
}

# Will wrangle each participant's data independently to see details of their runs
df_13 <- bind_rows(lapply(csv_files[1],read_csv_as_character))
df_15 <- bind_rows(lapply(csv_files[2],read_csv_as_character))
df_16 <- bind_rows(lapply(csv_files[3],read_csv_as_character))
df_18 <- bind_rows(lapply(csv_files[4],read_csv_as_character))
df_19 <- bind_rows(lapply(csv_files[5],read_csv_as_character))
df_21 <- bind_rows(lapply(csv_files[6],read_csv_as_character))
df_22 <- bind_rows(lapply(csv_files[7],read_csv_as_character))
```
**pre-processing the data**
First I will anonymize the data and remove unneccesary columns:
``` {r data_wrangling}
anonymize_clean <- function(df) {
  df <- df %>%
    select(-recorded_at,-ip,-user_agent,-referer,-sequence_length,
         -accept_language,-device,-internal_node_id,-view_history,
         -source_code_version, -contains("browser"),-contains("platform"),
         -contains("screen"),-contains("width"),-contains("height"),
         -contains("failed"),-condition,-success,-timeout,-event_history)
  return(df)
}
# df_list <-  list(df_13,df_15,df_16,df_18,df_19,df_21,df_22)
# df_list <- lapply(df_list, anonymize_clean)
df_13 <- anonymize_clean(df_13)
df_15 <- anonymize_clean(df_15)
df_16 <- anonymize_clean(df_16)
df_18 <- anonymize_clean(df_18)
df_19 <- anonymize_clean(df_19)
df_21 <- anonymize_clean(df_21)
df_22 <- anonymize_clean(df_22)
```

Now I will take out the practice trials and save them to a different df, I will also remove practice and all other trial types (other than sr or gradcpt) from my dataframe
``` {r data_wrangling}
save_practice <- function(df1, df2, df3, df4, df5, df6, df7) {
  practice_list <- list(df1, df2, df3, df4, df5, df6, df7)
  
  for (i in seq_along(practice_list)) {
    practice_list[[i]] <- practice_list[[i]] %>%
      filter(practice == "true")
  }
  
  return(practice_list)
}

practice_runs_df <- save_practice(df_13, df_15,df_16,df_18,df_19,df_21,df_22)


# remove irrelevant rows from main analysis dfs
# parse bid values
remove_non_game <- function(df) {
  df <- df %>%
    filter(trial_type != "instructions", trial_type != "preload", 
           trial_type != "survey-multi-choice", 
           trial_type != "html-keyboard-response",
           !grepl("screen", trial_type, ignore.case = TRUE)) %>%
    filter(practice != "true") %>%
    mutate(bid_value = as.integer(gsub("[^0-9]+", "", response))) 
  
  return(df)
}

df_13_sub <- remove_non_game(df_13)
df_15_sub <- remove_non_game(df_15)
df_16_sub <- remove_non_game(df_16)
df_18_sub <- remove_non_game(df_18)
df_19_sub <- remove_non_game(df_19)
df_21_sub <- remove_non_game(df_21)
df_22_sub <- remove_non_game(df_22)
```

this is a test, can ignore:
``` {r data_wrangling}

df_22_test <- df_22_sub

sr_practice_num <- 6
sr_per_block <- 8
gradcpt_practice_num <- 30
gradcpt_per_block <- 40
num_blocks <- 8

new_first_row <- data.frame(
  bid_value = NA,
  switch_next_block = NA,  # Replace with your initial switch_next_block if needed
  blocks_completed = '0',  # Replace with your initial blocks_completed
  prevBlockType = NA,  # Replace with an appropriate value if needed
  game_type = NA,  # Replace with an appropriate value if needed
  trial_type = "survey-text",
  trial_index = NA,
  time_elapsed = NA
)

# spatial recall!
df_22_test_res_sr <- df_22_test %>%
  filter(cpt_type != "transition") %>%
  filter((prevBlockType == "spatial_recall" & 
                              switch_next_block == "false") |
                    (prevBlockType == "gradcpt" & switch_next_block == "true")
       | (game_type == "spatial_recall"))

if (nrow(df_22_test_res_sr) > 0 && df_22_test_res_sr$trial_type[1] != "survey-text"){
  print("added now")
  df_22_test_res_sr <- df_22_test_res_sr %>% add_row(blocks_completed = '0', trial_type = 'survey-text', .before = 0)
}

df_22_test_res_sr <- df_22_test_res_sr %>%
  mutate(switch_next_block = ifelse(switch_next_block == "", NA, switch_next_block),group = rep(1:(n() %/% (sr_per_block + 1) + 1), each = (sr_per_block + 1), length.out = n())) %>%
  group_by(group) %>%
  mutate(switch_next_block = as.character(switch_next_block)) %>%
  fill(bid_value, switch_next_block,blocks_completed, .direction = "down") %>%
  ungroup() %>%
  select(-group,-bonus,-overall_accuracy,-cpt_practice_accuracy,-score_pc,-score_ls)

# gradcpt
df_22_test_res_cpt <- df_22_test %>%
  filter(cpt_type != "transition") %>%
  filter((prevBlockType == "gradcpt" & 
                                switch_next_block == "false") |
                      (prevBlockType == "spatial_recall" & switch_next_block == "true")
         | (game_type == "gradcpt")) 

if (nrow(df_22_test_res_cpt) > 0 && df_22_test_res_cpt$trial_type[1] != "survey-text"){
  df_22_test_res_cpt <- df_22_test_res_cpt %>% add_row(blocks_completed = '0', trial_type = 'survey-text', .before = 0)
}

df_22_test_res_cpt <- df_22_test_res_cpt %>%
  mutate(switch_next_block = ifelse(switch_next_block == "", NA, switch_next_block),group = rep(1:(n() %/% (gradcpt_per_block + 1) + 1), each = (gradcpt_per_block + 1), length.out = n())) %>%
  group_by(group) %>%
  mutate(switch_next_block = as.character(switch_next_block)) %>%
  fill(bid_value, switch_next_block,blocks_completed, .direction = "down")%>%
  ungroup() %>%
  select(-group,-bonus,-overall_accuracy,-cpt_practice_accuracy,-score_pc,-score_ls)

new_fin <- bind_rows(df_22_test_res_sr,df_22_test_res_cpt) %>%
  arrange(blocks_completed)
```


Now I'm going to distribute the bid value to its corresponding block for each df. I will also record which block each group of trials is, remove unneccary columns, and change the datatypes of necessary columns (i.e. subject id).
``` {r data_wrangling}
# spread bid and blocks completed value onto the entire block
# this new column will be how much the participant bid 
bid_val_dev <- function(df) {
  sr_practice_num <- 6
  sr_per_block <- 8
  gradcpt_practice_num <- 30
  gradcpt_per_block <- 40
  num_blocks <- 8
  
  df_test <- df
  
  # get run id of current df
  run_id = df$run_id[[1]]
  
  # spatial recall
  sr <- df_test %>%
    filter(cpt_type != "transition") %>%
    filter((prevBlockType == "spatial_recall" & 
                                switch_next_block == "false") |
                      (prevBlockType == "gradcpt" & switch_next_block == "true")
         | (game_type == "spatial_recall"))

  if (nrow(sr) > 0 && sr$trial_type[1] != "survey-text"){
    print("adding sr row")
    sr <- sr %>% add_row(blocks_completed = '0', trial_type = 'survey-text',run_id = as.character(run_id), .before = 0)
  }
  
  sr <- sr %>%
    mutate(switch_next_block = ifelse(switch_next_block == "", NA, switch_next_block),group = rep(1:(n() %/% (sr_per_block + 1) + 1), each = (sr_per_block + 1), length.out = n())) %>%
    group_by(group) %>%
    mutate(switch_next_block = as.character(switch_next_block)) %>%
    fill(bid_value, switch_next_block,blocks_completed, .direction = "down") %>%
    ungroup() %>%
    select(-group,-bonus,-overall_accuracy,-cpt_practice_accuracy,-score_pc,-score_ls)
  
  # gradcpt
  cpt <- df_test %>%
    filter(cpt_type != "transition") %>%
    filter((prevBlockType == "gradcpt" & 
                                  switch_next_block == "false") |
                        (prevBlockType == "spatial_recall" & switch_next_block == "true")
           | (game_type == "gradcpt")) 

  if (nrow(cpt) > 0 && cpt$trial_type[1] != "survey-text"){
    print("adding cpt row")
    cpt <- cpt %>% add_row(blocks_completed = '0', trial_type = 'survey-text', run_id = as.character(run_id),.before = 0)
  }

  cpt <- cpt %>%
    mutate(switch_next_block = ifelse(switch_next_block == "", NA, switch_next_block),group = rep(1:(n() %/% (gradcpt_per_block + 1) + 1), each = (gradcpt_per_block + 1), length.out = n())) %>%
    group_by(group) %>%
    mutate(switch_next_block = as.character(switch_next_block)) %>%
    fill(bid_value, switch_next_block,blocks_completed, .direction = "down")%>%
    ungroup() %>%
    select(-group,-bonus,-overall_accuracy,-cpt_practice_accuracy,-score_pc,-score_ls)
  
  final_df <- bind_rows(sr,cpt)
  
  return(final_df)
}
df_13_sub <- bid_val_dev(df_13_sub)
df_15_sub <- bid_val_dev(df_15_sub)
df_16_sub <- bid_val_dev(df_16_sub)
df_18_sub <- bid_val_dev(df_18_sub)
df_19_sub <- bid_val_dev(df_19_sub)
df_21_sub <- bid_val_dev(df_21_sub)
df_22_sub <- bid_val_dev(df_22_sub)

```

``` {r data_wrangling}
# assign block numbers
block_num_parse_vals <- function(df) {
  df <- df %>%
    mutate(subj_id = as.numeric(run_id), blocks_completed = as.numeric(blocks_completed,na.RM = TRUE)) %>%
    select(-run_id,-generated_BDM_value,-question_order) %>%
    mutate(curr_block_num = blocks_completed + 1) 
  
  return(df)
}
df_13_sub <- block_num_parse_vals(df_13_sub)
df_15_sub <- block_num_parse_vals(df_15_sub)
df_16_sub <- block_num_parse_vals(df_16_sub)
df_18_sub <- block_num_parse_vals(df_18_sub)
df_19_sub <- block_num_parse_vals(df_19_sub)
df_21_sub <- block_num_parse_vals(df_21_sub)
df_22_sub <- block_num_parse_vals(df_22_sub)
```

Now I will combine all of the participants cleaned data into one df, and will calculate average accuracy per block, average bid offer, stdev of bid offers,
z-score per bid offer. I also wanted to make a column for following_bid (the bid that followed a block)
``` {r data_wrangling}
total_data <- bind_rows(df_13_sub,df_15_sub,df_16_sub,df_18_sub,df_19_sub,df_21_sub,df_22_sub) %>%
  # filter(trial_type != "survey-text") %>%
  arrange(subj_id, curr_block_num) %>%
  rename(preceding_bid = bid_value)

bid_vals <- total_data %>%
  filter(trial_type == "survey-text") %>%
  group_by(subj_id) %>%
  arrange(subj_id,blocks_completed) %>%
  mutate(following_bid = lead(preceding_bid))

total_data <- total_data %>%
  left_join(bid_vals %>% select(subj_id, curr_block_num, following_bid),
            by = c("subj_id","curr_block_num"))
```

``` {r data_wrangling}
# get average bids per participant
avg_subj_bids <- total_data %>%
  filter(trial_type == "survey-text") %>%
  group_by(subj_id) %>%
  summarise(avg_bids = mean(preceding_bid,na.rm = TRUE),stdev_bids = sd(preceding_bid, na.rm = TRUE)) %>%
  ungroup()
total_data <- total_data %>%
  left_join(avg_subj_bids, by = "subj_id")

# make a column that represents how different (in stdev) the amount they want to switch is from their mean
total_data <- total_data %>%
  mutate(preceding_bid_z_score = if_else(stdev_bids == 0, 0, 
                                         ifelse(is.na(preceding_bid),0,
                                                ((preceding_bid - avg_bids) / 
                                                   stdev_bids))),
         following_bid_z_score = if_else(stdev_bids == 0, 0, 
                                         ifelse(is.na(following_bid),0,
                                                ((following_bid - avg_bids) / stdev_bids)))) %>%
  filter(trial_type != "survey-text") %>%
  select(-time_elapsed,-response,-sequence,-backwards,-responses,-practice,
         -correct_key,-curr_level,-curr_trial_duration,-cpt_type,-prevBlockType,
         -preceding_bid,-following_bid,-avg_bids,-stdev_bids) %>%
  rename(block_switched=switch_next_block)
```

Now I will calculate average accuracy per block.
``` {r data_wrangling}
# conversion dict for gradcpt
conversion <- c("true" = 1, "false" = 0)

avg_spatial_recall <- total_data %>%
  filter(game_type == "spatial_recall") %>%
  group_by(subj_id, curr_block_num) %>%
  summarise(avg_accuracy = mean(as.numeric(score_an), na.rm = TRUE),stdev_accuracy = sd(as.numeric(score_an),na.rm = TRUE))%>%
  arrange(subj_id,curr_block_num)

avg_cpt <- total_data %>%
  filter(game_type == "gradcpt") %>%
  group_by(subj_id, curr_block_num) %>%
  summarise(avg_accuracy = mean(conversion[correct], na.rm = TRUE),stdev_accuracy = sd(conversion[correct],na.rm=TRUE))

avg_per_block <- bind_rows(avg_spatial_recall, avg_cpt) %>%
  arrange(subj_id, curr_block_num)
```

Now I will join these values into my total dataset.
``` {r data_wrangling}
total_data <- total_data %>%
  left_join(avg_per_block, by = c("subj_id","curr_block_num"))
```

**analyzing and plotting the data**

Plotting bids over time:
``` {r data_wrangling}
bid_block_total <- total_data %>%
  select(subj_id,curr_block_num,blocks_completed,following_bid_z_score,
         preceding_bid_z_score,avg_accuracy,stdev_accuracy) %>%
  group_by(subj_id,curr_block_num,blocks_completed,avg_accuracy,stdev_accuracy) %>%
  summarise(avg_following_bid_z = mean(following_bid_z_score),
            avg_preceding_bid_z = mean(preceding_bid_z_score))

# faceted by subject
bid_block_total %>%
  mutate(subj_id = as.factor(subj_id)) %>%
  ggplot(mapping = aes(x=curr_block_num,y=avg_following_bid_z,fill=subj_id,color=subj_id)) +
  geom_point(alpha = 0.3,
             position = position_jitter(height = 0, width = 0.1)) +
  facet_wrap(~subj_id) +
  geom_smooth(method="lm",se=TRUE) +
  labs(x = "Block number", 
       y = "Z-scored bid offer (relative to each subject's avg and sd)", 
       title = "Bid offers following each block, by subject")

# not faceted by subject
bid_block_total %>%
  mutate(subj_id = as.factor(subj_id)) %>%
  group_by(curr_block_num) %>%
  ggplot(mapping = aes(x=curr_block_num,y=avg_following_bid_z,fill=subj_id,color=subj_id)) +
  geom_point(alpha = 0.3,
             position = position_jitter(height = 0, width = 0.1)) +
  geom_smooth(method="lm",se=TRUE) +
  labs(x = "Block number", 
       y = "Z-scored bid offer (relative to each subject's avg and sd)", 
       title = "Bid offers following each block, by subject")

# averaged across all participants
bid_block_total %>%
  group_by(curr_block_num) %>%
  ggplot(mapping = aes(x=curr_block_num,y=avg_following_bid_z)) +
  geom_point(alpha = 0.3,
             position = position_jitter(height = 0, width = 0.1)) +
  geom_smooth(method="lm",se=TRUE) +
  labs(x = "Block number", 
       y = "Z-scored bid offer (relative to each subject's avg and sd)", 
       title = "Bid offers following each block, by subject")
```

Plotting preceding bid by avg accuracy in following block:
``` {r data_wrangling}


```
Plotting following bid by avg accuracy in a block:

``` {r data_wrangling}


```
Plotting avg accuracies in spatial recall vs gradcpt:

``` {r data_wrangling}


```

Facet by switch or not
``` {r data_wrangling}


```
