---
title: "study2_testBatchAnalysis"
output: html_document
date: "2025-01-14"
---
This is the first analysis for study 2, to ensure the data of the first 9 people are correct. Subject 13 and 14 have the final data correctly written down (the additional columns), but the other subjects all have the same experiment just not some additional cols; also 13,14, and all before did not have RT for digit span. Only subjects 20 and 22 have all of the necessary columns, even though all 9 have the same experiment.

Goal for this simple analysis: 
- make sure that for subj 20 and 22, rt is analyzable and correct
- make sure that for subj 13,14,20,22 the additional columns are correct and can be analyzable
- plot the distribution of rt for both tasks for the 2 subjects whose data got captured properly
- plot the distribution of correctness for both tasks for the 4 subjects whose data got captured properly
- plot rest length over time per participant 

The setup was:
4 spatial recall practice
4 digit span practice
4 rest practice

10 groups, 13 blocks per group
- 10 digit span per block
- 10 visual search per block
- up to 20 rest per rest period

group ordering: ABABBABAAB

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
##library(jsonlite)
library("broom")      # for tidying up linear models 
library("car")        # for running ANOVAs
library("afex")       # also for running ANOVAs
library("emmeans")    # for calculating constrasts

# set the default ggplot theme 
theme_set(theme_classic())
```

**reading in the data**
``` {r data_wrangling}
# setwd("../../data/pilotE_SPR_testBatch")
setwd("../../data/pilotE_SPR_testBatch2")

csv_files <- list.files(pattern = "\\.csv$")

# Function to read a CSV file and convert all columns to character type
read_csv_as_character <- function(file) {
  df <- read.csv(file, stringsAsFactors = FALSE)
  df[] <- lapply(df, as.character)
  return(df)
}

df_all <- bind_rows(lapply(csv_files,read_csv_as_character))
```

**pre-processing the data**

Anonymize the data and remove unneccesary columns:
``` {r data_wrangling_anon}
anonymize_clean <- function(df) {
  df <- df %>%
    select(-recorded_at,-url,-ip,-user_agent,-referer,-sequence_length,
         -accept_language,-device,-internal_node_id,-view_history,
         -source_code_version, -contains("browser"),-contains("platform"),
         -contains("screen"),-contains("width"),-contains("height"),
         -contains("failed"),-condition,-success,-event_history)
  return(df)
}
df_all <- anonymize_clean(df_all)
```


Take the two subjects that have the most updated data (subj 13 and 14) and the two with the added digit span RT (subj 20 and 22)
``` {r data_wrangling_anon}
df_all <- df_all %>%
  mutate(subj_id = as.integer(run_id)) %>%
  select(-run_id)

df_recent_subset <- df_all 

# df_recent_subset <- df_all %>%
#   filter(subj_id == 13 | subj_id == 14 | subj_id == 20 | subj_id == 22)
```

Save the practice runs in a separate df, and also change is_correct into a true/false, calculate avg performance on each task, get rid of unnecessary columns
``` {r data_wrangling_anon}
df_recent_subset <- df_recent_subset %>%
  mutate(is_correct_numeric = ifelse(is_correct=="true", 1, 0)) %>%
  filter(trial_type == "sr_practice_response" | trial_type == "ds_practice_response" | trial_type == "rt_practice_trials" | trial_type == "sr_main_response" | trial_type == "ds_main_response" | trial_type == "dsst-with-end-rest" | trial_type == "rt_main_trials") %>%
  mutate(trial_type_name = ifelse(trial_type == "dsst-with-end-rest", "rt_main_trials", trial_type)) %>%
  mutate(trial_type = trial_type_name) %>%
  select(-c(trial_type_name, gameA_name, gameB_name, gameA_isSR, game_A, game_B, backwards, score_an, score_pc, score_ls, is_correct, stimulus, target_shape, final_bonus)) %>%
  arrange(subj_id)

practice_runs_subset_df <- df_recent_subset %>%
  filter(trial_type == "sr_practice_response" | trial_type == "ds_practice_response" | trial_type == "rt_practice_trials") %>%
  group_by(subj_id, trial_type) %>%
  summarize(avg_accuracy = mean(is_correct_numeric))

all_runs_avg_subset <- df_recent_subset %>%
  filter(trial_type == "sr_main_response" | trial_type == "ds_main_response" | trial_type == "rt_main_trials") %>%
  group_by(subj_id, trial_type) %>%
  summarize(avg_accuracy = mean(is_correct_numeric))

# write.csv(df_recent_subset, "cleaned_data_test.csv") # for reference/brainstorming -> delete before github
```


Add block labels to each block, and group numbers to each group
Will do: 1,2,3,4,5,6,etc so up to 30 for the blocks
``` {r data_wrangling_anon}
# exp vars
sr_practice_num <- 4
sr_per_block <- 10
ds_practice_num <- 4
ds_per_block <- 10
rt_practice_num <- 4
rt_per__block_max <- 20
num_groups <- 10
num_blocks_per_group <- 3
num_blocks_overall <- num_groups * num_blocks_per_group

# make sure its arranged in order
df_recent_subset_analyze <- df_recent_subset %>%
  filter(trial_type != "sr_practice_response" & trial_type != "ds_practice_response" & trial_type != "rt_practice_trials") %>%
  mutate(trial_index_num = as.numeric(trial_index)) %>%
  mutate(trial_index = trial_index_num) %>%
  select(-trial_index_num) %>%
  arrange(subj_id, trial_index) %>%
  ungroup()

# add overall trial counts of each task
df_recent_subset_analyze <- df_recent_subset_analyze %>%
  group_by(subj_id, game_type) %>%
  arrange(trial_index) %>%
  mutate(overall_type_count = row_number()) %>%
  ungroup() %>%
  arrange(subj_id, trial_index)

# add the block numbers and group values
df_recent_subset_analyze <- df_recent_subset_analyze %>%
  arrange(subj_id, trial_index) %>%
  group_by(subj_id) %>%
  mutate(
    block_num = cumsum(game_type == "rest_task" & lag(game_type, default = first(game_type)) != "rest_task"),
    group_num = ifelse(game_type == "rest_task" & follows_group_num != "null", follows_group_num, NA)
  ) %>%
  fill(group_num, .direction = "up") %>%
  mutate(
    # block_num = ifelse(game_type == "rest_task", NA, block_num),
    block_num = ifelse(is.na(block_num), 1, block_num)
  ) %>%
  ungroup()

# reset the block numbers to start from 1 for each participant
# get rid of group num for rest task
df_recent_subset_analyze <- df_recent_subset_analyze %>%
  group_by(subj_id) %>%
  mutate(
    block_num = ifelse(block_num >= 0, dense_rank(block_num), block_num),
    block_num = ifelse(game_type == "rest_task", NA, block_num)
  ) %>%
  select(-transition_type, -option_to_end, -overall_num_rest_used, -end_rest_button_clicked, -responses, -timeout) %>%
  ungroup() %>%
  arrange(subj_id, trial_index)

```

## Basic Plots and Checks:

Plot average accuracies per task per person:
``` {r avg_acc_pre_exclusion}
all_runs_avg_subset %>%
  ggplot(aes(x=trial_type,y=avg_accuracy,color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  # facet_wrap(~trial_type)+
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game types",y="Average accuracy per participant on given game type")+
  ggtitle("Average participant performance on each game: pre-exclusion")

```


Plot average RT per task per person:
``` {r avg_rt_pre_exclusion}
df_recent_subset_analyze <- df_recent_subset_analyze %>%
  mutate(timed_out = ifelse(timed_out == "true" | timed_out == 1, TRUE, FALSE)) %>%
  mutate(rt = ifelse(timed_out == TRUE & game_type == "rest_task",5000,rt)) %>%
  # mutate(rt = ifelse(timed_out == TRUE,-1,rt)) %>%
  mutate(rt_num = as.numeric(rt)) %>%
  mutate(rt = rt_num) %>%
  select(-rt_num)

df_recent_subset_analyze %>%
  filter(rt >= 4000 & response != "null" & response != "[]")

rt_overall_avgs <- df_recent_subset_analyze %>%
  ungroup() %>%
  filter(timed_out == FALSE) %>%
  group_by(subj_id, game_type) %>%
  summarize(rt_avg = mean(rt))

rt_overall_avgs %>%
  ggplot(aes(x=game_type,y=rt_avg,color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  # facet_wrap(~trial_type)+
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game types",y="Average rt per participant on given game type")+
  ggtitle("Average participant rt on each game: pre-exclusion")



df_recent_subset_analyze <- df_recent_subset_analyze %>%
  select(-correct_response, -rest_trial_num, -end_rest)
```


Plot performance over time SR and DS and Rest Task per person:
``` {r perf_over_time_pre_exclusion}
avg_accuracy_blocks <- df_recent_subset_analyze %>%
  ungroup() %>%
  group_by(subj_id, block_num, group_num, game_type) %>%
  summarise(avg_accuracy = mean(is_correct_numeric))

avg_accuracy_blocks %>%
  filter(game_type == "spatial_recall") %>%
  ggplot(mapping = aes(x=block_num, y=avg_accuracy, color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  geom_smooth(method = "lm", se = TRUE) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  ylim(0,1) +
  # stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Block number",y="Average accuracy per participant in given block")+
  ggtitle("Spatial recall: Average accuracy over time: pre-exclusion")



avg_accuracy_blocks %>%
  filter(game_type == "digit_span") %>%
  ggplot(mapping = aes(x=block_num, y=avg_accuracy, color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  geom_smooth(method = "lm", se = TRUE) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  ylim(0,1) +
  # stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Block number",y="Average accuracy per participant in given block")+
  ggtitle("Digit span: Average accuracy over time: pre-exclusion")



avg_accuracy_blocks %>%
  filter(game_type == "rest_task") %>%
  mutate(group_num = as.numeric(group_num)) %>%
  ggplot(mapping = aes(x=group_num, y=avg_accuracy, color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  geom_smooth(method = "lm", se = TRUE,formula = y ~ x) +
  ylim(0,1) +
  # stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Group number",y="Average accuracy per participant in given group")+
  ggtitle("Rest task: Average accuracy over time: pre-exclusion")


```

Plot rests taken over time:
``` {r rests_over_time_pre_exclusion}
df_recent_subset_analyze <- df_recent_subset_analyze %>%
  ungroup() %>%
  arrange(subj_id, trial_index) %>%
  group_by(subj_id) %>%
  mutate(task_change = game_type != lag(game_type, default = "first_row"),
         rest_chunk = cumsum(task_change & game_type == "rest_task"),
         rest_chunk = ifelse(game_type == "rest_task", rest_chunk, NA)) %>%
  ungroup() %>%
  group_by(subj_id, rest_chunk) %>%
  mutate(num_rest_in_chunk = sum(!is.na(rest_chunk))) %>%
  select(-task_change) %>%
  ungroup()


df_recent_subset_analyze %>%
  filter(game_type == "rest_task") %>%
  select(subj_id, rest_chunk, num_rest_in_chunk) %>%
  group_by(subj_id, rest_chunk, num_rest_in_chunk) %>%
  distinct() %>%
  ungroup() %>%
  ggplot(mapping = aes(x=rest_chunk, y=num_rest_in_chunk, color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  geom_smooth(method = "lm", se = TRUE,formula = y ~ x) +
  labs(x="Rest period number",y="Number of rests taken")+
  ggtitle("Average number of rests taken over time: pre-exclusion")
  
```


Plot average proportion of timeouts per task:
``` {r rests_over_time_pre_exclusion}
df_recent_subset_analyze %>%
  ungroup() %>%
  group_by(subj_id, game_type) %>%
  summarize(num_timed_out = sum(timed_out == TRUE), num_not_timed_out = sum(timed_out == FALSE)) %>%
  mutate(total_trials = num_not_timed_out + num_timed_out,
         prop_timed_out = num_timed_out / total_trials) %>%
  ggplot(mapping = aes(x=game_type, y=prop_timed_out, color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  labs(x="Game type",y="Proportion of trials timed out")+
  ggtitle("Proportion of trials timed out, per game type: pre-exclusion")
```


